\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{positioning,arrows.meta,shapes.geometric,backgrounds,fit,calc}

\bibliographystyle{plain}
\usepackage{doi}

\geometry{margin=2.4cm}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!60!black,
  citecolor=blue!60!black,
  urlcolor=blue!60!black
}

\newcommand{\Heis}{\mathrm{Heis}}
\newcommand{\SU}{\mathrm{SU}}
\newcommand{\BI}{\mathrm{BI}}
\definecolor{cproved}{RGB}{30,140,60}
\definecolor{cstruct}{RGB}{40,100,200}
\definecolor{cheur}{RGB}{200,130,0}
\definecolor{copen}{RGB}{190,50,40}
\newcommand{\sproved}{\textcolor{cproved}{\textbf{proved}}}
\newcommand{\sstruct}{\textcolor{cstruct}{\textbf{structural}}}
\newcommand{\sheur}{\textcolor{cheur}{\textbf{heuristic}}}
\newcommand{\sopen}{\textcolor{copen}{\textbf{open}}}

\title{The Cosmochrony Research Programme:\\[4pt]
A Structural Roadmap and Paper Inventory}

\author{J\'er\^ome Beau\\[4pt]
\small Independent Researcher\\
\small \texttt{jerome.beau@cosmochrony.org}}

\date{2026}

\begin{document}

  \maketitle

  \begin{abstract}
    The Cosmochrony programme develops a pre-geometric framework in which physical structure ---
    spacetime, quantum mechanics, gauge symmetry, and Standard Model observables --- arises from
    a single primitive: the local structure of admissible non-injective transitions between observable states.
    The corpus comprises 71 papers across three theory branches.
    Branch~I (Foundation track) builds the axiomatic base: four axioms suffice to derive the
    Heisenberg group $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ and its Weil representation as theorems, without
    any background substrate or relaxation mechanism.
    Branch~II (O-series) develops the spectral admissibility sub-programme, deriving and numerically
    validating the transfer chain $c_\chi \to \delta_{\mathrm{pair}} \to \beta^* \approx 0.126$
    connecting the BI saturation constant to the charged-lepton mass hierarchy.
    Branch~III (Q-series and companion papers) derives quantum mechanics, spacetime geometry,
    gauge structure, and further physical observables from Branch~I axioms and Branch~II spectral data.
    Paper Q3 completes the $\SU(2)$ quantum sector: by combining BI indiscernibility with
    Schur's lemma on the Clebsch--Gordan decomposition of $\chi_{2j+1}\otimes\chi_{2j+1}$, the
    universal singlet correlator $E(\hat{a},\hat{b}) = -j(j+1)/3\cdot(\hat{a}\cdot\hat{b})$ and the
    Born rule are derived for all five admissible sectors of~$2I$, closing the general-$j$ extension
    that was open in~Q2.
    The geometric emergence sub-programme (Q5a--Q10, U1, W1, H2) closes the effective spacetime
    identification: under the Q5a continuum-limit hypotheses, the lifting hypothesis~[H-lift]
    is proved (Q9), asymptotic $\mathfrak{su}(2)$-isotropy $A_H \to 2$ is proved (Q10, U1),
    the admissibility weight convergence~[H-w] is proved (W1),
    yielding the effective Lorentzian co-metric
    $g^{\mu\nu} = \mathrm{diag}(-2, 2, 2, 2) \propto \eta^{\mu\nu}$ ($A_\tau = 2$, Q11~\cite{Beau2026q11}).
    Q5a v2.0 establishes that [H1] is not needed in full generality.
    Q5a-O2~\cite{Beau2026q5ao2} proves spectral atomicity of the admissible sector
    (each pair spans three pure Fourier modes)
    and closes hypotheses [H-$\mathcal{E}$1] and [C] without Nash inequalities.
    Hypothesis~[H2] (strong convergence of the rescaled Weil generators) is proved (H2~paper),
    closing all hypotheses of the Q5a large-$q$ convergence theorem unconditionally on the admissible sector.
    O31 develops the structural framework for the SU(3) identification: the metaplectic
    intertwining of $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ forces triplet co-admissibility
    unconditionally for the colour-adapted Cayley graph, and SU(3) is thereby identified as the
    symmetry group of the co-admissible colour triplet conditional on~[H-color].
    This paper provides a complete inventory, a logical dependency map, and a structured account
    of what is proved, structural, heuristic, or open.
    It is intended both as an entry point for external readers and as an internal navigation reference.
  \end{abstract}

  \paragraph{Keywords.}
    Non-injective projection; admissibility; Born--Infeld constraint; spectral admissibility;
    Heisenberg group; Weil representation; emergent spacetime; lepton mass hierarchy;
    quantum mechanics; gauge structure; programme overview.

    \clearpage

    \setcounter{tocdepth}{2}
    \tableofcontents

    \clearpage

  \section{Introduction and Purpose}

  The Cosmochrony programme was initiated with a white paper~\cite{Cosmochrony} positing that
  all physical structure emerges from a non-injective projection $\Pi : \Omega \to \mathcal{O}$
  from a pre-geometric substrate $\chi$ onto observable space.
  The initial framework postulated a Born--Infeld (BI) saturation constraint, a relaxation mechanism,
  and an iterated projection cascade $U_{t+1} = \Pi \circ \sigma(U_t)$ as the engine of dynamics.

  Over the course of 2026, the programme has evolved in two parallel directions.
  On one side, the spectral admissibility sub-programme (O-series, papers O1--O28) has progressively
  built the computational machinery for extracting physical observables from the spectral structure
  of the substrate, culminating in the proof of the unconditional transfer chain in O24~\cite{Beau2026a28}.
  On the other side, the Foundation paper~\cite{Beau2026m} has refounded the entire framework from
  four axioms~(A1--A4), dispensing with any explicit substrate $\chi$ and relaxation mechanism:
  these emerge as consequences of the axiomatic structure rather than being postulated.
  The Q-series then builds quantum mechanics, $\SU(2)$ symmetry, and Lorentzian spacetime
  on top of the Foundation axioms and O-series spectral data.

  The corpus comprises 71 papers with complex mutual dependencies.
  A reader entering the programme faces two difficulties: it is not obvious where to start,
  and the distinction between a theorem, a structural argument, and an open conjecture is not always
  transparent from individual paper titles.
  This roadmap addresses both difficulties.

  \paragraph{Conventions on result status.}
    Throughout this paper each result is classified as one of the following:
    \sproved{} (formally proved as a theorem within the stated assumptions);
    \sstruct{} (derived from structural arguments that are internally consistent but not yet fully
    formalised);
    \sheur{} (physically motivated and numerically supported but not yet rigorously derived);
    \sopen{} (explicitly conjectured or known to be unsettled).
    These classifications follow the original papers; this roadmap introduces no new claims.

  \section{Conceptual Architecture}
  \label{sec:architecture}

  The programme is organised in three structural levels.

  \paragraph{Level 1 --- Axiomatic primitive.}
    The primitive is the local structure of admissible non-injective transitions.
    No background spacetime, no quantum postulate, and no substrate field are introduced at this level.
    The four axioms are: local projective admissibility~(A1), structural non-injectivity~(A2),
    admissibility as non-premature selection~(A3), and projection locking~(A4).
    From~A1--A2 alone, irreversibility and the arrow of time follow.
    From~A3, the Heisenberg non-commutativity and the Weil representation emerge.
    From~A4, the discreteness of quantum transitions follows.
    Papers at this level: ENI~\cite{Beau2026l}, Foundation~\cite{Beau2026m},
    HeisenbergStructure, noscale~\cite{Beau2026j}.

  \paragraph{Level 2 --- Spectral fibre structure.}
    The admissible fibre is proved to carry the Weil representation $V_\rho$ of
    $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ for a prime~$q$ (Foundation Theorem~5.6;
    detailed proof in HeisenbergStructure~\cite{Beau2026HeisenbergStructure}).
    The O-series computes the spectral properties of this fibre --- in particular the capacity
    exponent $\delta_{\mathrm{pair}}$ and its transfer to the cascade exponent $\beta^*$ governing
    the charged-lepton mass hierarchy.
    Papers at this level: SpectralAdmissibility~\cite{Beau2026a1},
    SpectralCapacity~\cite{Beau2026a2},
    SpectralGramRigidity~\cite{Beau2026a3}, SpectralRelaxation~\cite{Beau2026a5},
    and O1--O31~(\cite{Beau2026a6}--\cite{Beau2026a35}).

  \paragraph{Level 3 --- Physical observables.}
    Effective spacetime geometry, gauge structure, Standard Model charges and masses, gravitational
    waves, and cosmological observables are derived as consequences of Levels~1--2.
    No additional physical postulates are introduced beyond the continuum-limit hypotheses of Q5a--Q5b.
    Papers at this level: the Q-series (Q1~\cite{Beau2026q1}, Q2~\cite{Beau2026q2},
    Q3~\cite{Beau2026q3}, Q5a--Q7), the gravity track
    (Spectral2~\cite{Beau2026a}, Gravity~\cite{Beau2026h}, Thermodynamics, Lorentz~\cite{Beau2026i}),
    and the companion papers~(\cite{Beau2026b,Beau2026c,Beau2026d,Beau2026e,Beau2026f,Beau2026g,Beau2026k}).

  \section{Branch I: Axiomatic Foundations}
  \label{sec:foundations}

  \subsection{The White Paper}

    The white paper~\cite{Cosmochrony} (``Cosmochrony: A Non-Injective Projection Theory of Emergent
  Physics,'' v3.2) is the programme's primary overview document.
    It introduces the substrate field~$\chi$, the non-injective projection~$\Pi$, the BI saturation
    constraint, the relaxation mechanism, and the qualitative derivation of spacetime and quantum structure.
    The spectral entropy functional $S_\Pi[g] = \tfrac{1}{2}\log\det' A_g$ appears here as the
    structural origin of the Einstein equation.

    Version~3.2 incorporates several structural refinements informed by the O-series and Foundation
    results:
    \begin{itemize}
      \item \textit{Oriented state machine:} the admissible cascade is reformulated as a directed
        graph on admissible projections; physical histories are directed paths, and the first
        transition is guaranteed by non-commutativity $[X,\sigma(X)] = Z \neq 0$~\cite{Beau2026m}.
      \item \textit{Initial conditions dissolved:} the minimal state~$\chi_0$ cannot be a global
        minimum of the cascade; the fibre non-commutativity prevents any admissible projection from
        having trivial kernel, so the cascade begins as a structural necessity.
      \item \textit{Inaccessibility of absolute zero:} the Heisenberg structure of the admissible
        fibre forbids projective stasis $U_{n+1} = U_n$ at any stage.
      \item \textit{Algebraic necessity of fluctuations (Remark):} no admissible projection can have
        trivial kernel, so quantum vacuum fluctuations are a structural necessity, not a contingent
        feature.
      \item \textit{Schr\"{o}dinger as Mosco limit:} the continuous Schr\"{o}dinger equation is
        derived as the Mosco limit of the discrete oriented admissibility cascade.
      \item \textit{Extended numerical scope:} the PTO monotonicity is verified for
        $q \in \{29,61,101,151,211\}$, with~274 conjugate pairs and~360 post-burn-in steps.
    \end{itemize}

    \textit{Role:} Programme overview; structural motivation; first formulation of the BI constraint
    and the relaxation cascade.
    \textit{Evolution note:} The explicit substrate~$\chi$ and relaxation mechanism of the white paper
    are not postulated in the Foundation reformulation: they emerge from axioms~A1--A4.
    The white paper remains the primary narrative reference; Branch~I papers are the formal foundation.

  \subsection{Non-Injectivity as a Structural Necessity of Genuine Emergence}

    The ENI paper~\cite{Beau2026l} proves the following no-go theorem.
    Any genuinely emergent (non-isomorphic effective) physical description is necessarily non-injective
    and intrinsically compressive.
    The argument is purely structural: given a surjective $\Pi : \Omega \to \mathcal{O}$ such that
    $\mathcal{O}$ carries no independent microstate-resolving structure beyond~$\Pi$,
    non-isomorphism of levels forces non-injectivity.
    A projection entropy $S_\Pi \geq 0$ is defined, and the equivalence
    $\text{genuine emergence} \Leftrightarrow \Pi \text{ non-injective} \Leftrightarrow S_\Pi > 0$
    is established (\sproved, Theorem~2.1 and Corollary~3.1).

    \textit{Role:} Foundational justification for structural non-injectivity~(Axiom~A2).
    Version~2 adds Corollary~6 (recursive non-injectivity: any tower of genuinely
    distinct emergent levels carries one independent non-injective projection per stratum)
    and Section~5 (towers of emergence, structural colour confinement as projective
    necessity).
    A new Remark (algebraic route) shows that in frameworks whose fibre carries a Heisenberg
    algebra $[X,Y]=Z\neq 0$, $S_\Pi > 0$ also follows directly from fibre non-commutativity:
    a trivial-kernel projection would require simultaneous diagonalisation of $X$ and $Y$,
    which is structurally forbidden.
    The two derivations are complementary: Theorem~2.1 answers \emph{what} is forced
    (framework-independently); the algebraic route answers \emph{why} in Heisenberg-fibred frameworks.
    Cited by Foundation, HeisenbergStructure~\cite{Beau2026HeisenbergStructure},
    Q1~\cite{Beau2026q1}, Bell, O32~\cite{Beau2026a36}.

  \subsection{Foundation: Admissible Non-Injective Transitions as the Primitive}
    \label{sec:foundation}

    The Foundation paper~\cite{Beau2026m} (v1.10) establishes the minimal axiomatic basis of the programme.
    From the four axioms~A1--A4 alone it derives:
    (i) irreversibility and the arrow of time (A1+A2);
    (ii) the proto-state as a physically real unresolved configuration retaining phase coherence~(A3);
    (iii) a non-trivial commutator between conjugate generators, forced by~A3 and the minimality of~A1;
    (iv) the identification of the admissible fibre symmetry group as $\Heis_3(\mathbb{Z}/q\mathbb{Z})$
    for a prime~$q$, together with BI parity (A1--A3);
    (v) the identification $F_n \cong V_\rho$ (Weil representation) as a theorem (Theorem~5.6);
    (vi) the discrete character of quantum transitions from~A4;
    (vii) projective incompleteness (Corollary to Theorem~5.4): every admissible projection
    $\Pi_n$ has a non-trivial kernel, so no observable description is ever complete —
    a direct consequence of $[X, \sigma(X)] = Z \neq 0$.
    The paper also establishes the threefold role of~$\Pi_n$ (Remark~3.5):
    admissibility filter, generator of temporal order, and revelation operator —
    three roles that are algebraically inseparable and all sourced in the non-commutativity.
    v1.10 adds the co-metric result $g^{\mu\nu}=\mathrm{diag}(-2,2,2,2)$ (from Q5b,
    Q6b, Q8, Q10, Q11) to the results table, and a new section placing the
    four axioms relative to established formalisms
    (Hamilton--Jacobi, symplectic geometry, WKB, functional renormalisation group).

    \textit{Status:} \sproved{} for the algebraic identification of the fibre;
    \sstruct{} for the continuum limit (deferred to Q5a--Q5b).
    \textit{Role:} Axiomatic spine.
    Cited by all Q-series papers, HeisenbergStructure~\cite{Beau2026HeisenbergStructure}
    , noscale, and recent companion papers.

  \subsection{Non-Factorisability and the Emergence of Heisenberg Structure}

    HeisenbergStructure~\cite{Beau2026HeisenbergStructure}
    provides the detailed proof of Foundation Theorem~5.6, omitted from the
    Foundation paper for concision.
    The central structural lemma --- \emph{admissible non-factorisability} --- is a direct
    formalisation of Axiom~A3 and requires no input beyond~A1--A3, BI parity, and classical
    group-classification results.
    As a corollary, the Heisenberg uncertainty principle is derived as a structural property
    of the non-resolved proto-state, not as an independent postulate (\sproved).

    \textit{Role:} Detailed proof of the algebraic core; cited by Q1~\cite{Beau2026q1}, Q2~\cite{Beau2026q2}.

  \subsection{No External Dimensional Scale at the Level of Admissibility}

    The noscale paper~\cite{Beau2026j} establishes a structural rigidity result~(Level~1):
    any deformation of the admissibility constraints that introduces a dimensional parameter
    independent of~$c_\chi$ breaks at least one of BFS-consistent spectral scaling, structural
    non-injectivity~(A2/ENI), or bounded admissibility closure~(A3--A4).
    Dimensional analysis within the framework is therefore fully constrained by~$c_\chi$ alone (\sproved).

    \textit{Role:} Closes the naturalness question for dimensional parameters.

  \section{Branch II: Spectral Admissibility Sub-Programme (O-Series)}
  \label{sec:oseries}

  The O-series targets the derivation of the charged-lepton mass hierarchy from the spectral
  structure of the admissible fibre.
  The central quantity is the power-law exponent $\delta_{\mathrm{pair}}$ of the pair-level
  capacity observable $\sigma_{\mathrm{pair}}(n) = \sigma_c(n)\cdot\sigma_{q-c}(n)$ along
  the BFS cascade.
  The main transfer chain is
  \begin{equation}
    c_\chi \;\longrightarrow\; \delta_{\mathrm{pair}} \;\longrightarrow\; \beta^* \approx 0.126
    \;\longrightarrow\; m_e : m_\mu : m_\tau .
    \label{eq:chain}
  \end{equation}
  This chain is proved unconditionally with respect to the fibre structure of $\Pi$
  (O24~\cite{Beau2026a28}, Corollary~4.2).
  The numerical validation of~\eqref{eq:chain} is the subject of O25~\cite{Beau2026a29}.

  \subsection{Precursor Papers: SU(2) Admissibility Sub-Programme}

    Three papers precede the O-series proper and explore spectral admissibility on Cayley graphs
    of finite $\SU(2)$ subgroups.

    \textbf{SpectralAdmissibility}~\cite{Beau2026a1} (v2.0) carries out the spectral admissibility
    programme on two parallel chains.
    For the $\mathrm{SU}(2)$ chain $Q_8 \subset 2I \subset \mathrm{PSL}(2,\mathbb{F}_q)$, it derives
    the admissibility hierarchy $A^{\max}_n = c_\chi/\sqrt{\lambda_n}$ in the linearised regime and
    shows that the non-linear DBI correction preserves it.
    For the $\mathrm{SU}(3)$ chain $\Delta(27) \subset \Sigma(168)$, it establishes via character
    theory the hierarchy
    $\lambda_{\mathbf{3}} = \lambda_{\bar{\mathbf{3}}} = 28 < \lambda_{\mathbf{6}} = \lambda_{\mathbf{8}}
    = 42 < \lambda_{\mathbf{7}} = 48$
    on $\mathrm{Cay}(\Sigma(168), C_4)$, proving that the fundamental and anti-fundamental
    representations are co-admissible and strictly dominate all competitors.
    The algebraic mechanism is uniform: $\chi_{\mathbf{3}}(g) = 1$ for all $g \in C_4$ plays the
    same structural role as $\chi_{\rho_4} = 0$ on $Q_8$ and the golden-ratio identity on $2I$
    (\sproved).

    \textbf{SpectralCapacity}~\cite{Beau2026a2} introduces the capacity functional $\mathcal{C}(G,S)$
    and proves the binary-polyhedral maximality conjecture: the adjoint identity
    $\hat{A}_{\mathrm{adj}} = 2M - I$ (where $M$ is the second-moment tensor of the axis distribution)
    shows that icosahedral isotropy forces $\mu_{\mathrm{adj}}(2I) = -\tfrac{1}{3}$,
    while axis-plane confinement forces $\mu_{\mathrm{adj}}(\mathrm{Dic}_n) \geq 0$ for all $n \geq 3$;
    combined with a Plancherel uniform bound, this yields a strictly increasing capacity gap
    $\Delta(\alpha) > 0$ for all $\alpha > 0$ (\sproved).

    \textbf{SpectralGramRigidity}~\cite{Beau2026a3} (v1.0.1) shows that the geometry of neutral
    generating sets on $\SU(2)$ is fully encoded in pairwise character values
    $G_{st} = -\tfrac{1}{2}\chi_\rho(st)$ (\sproved).

    \textbf{Three Particle Generations}~\cite{Beau2026a4} derives the three-generation structure
    from the ADE stratigraphic levels of binary Cayley graphs (\sstruct).

  \subsection{SpectralRelaxation: Expander Graph Dynamics}

    The SpectralRelaxation paper~\cite{Beau2026a5} establishes $\Lambda_{\mathrm{proj}} \asymp \lambda_2$
    for LPS expander families (\sproved), providing the entry point for the O-series dynamics.

  \subsection{O1--O8: LPS Phase --- Cascade Exponent $\beta$}

    \textbf{O1}~\cite{Beau2026a6}: LPS saturation is a fixed-valence artefact; growing valence restores
    the pre-saturation window (\sproved).
    (Note: O2 was not written; the O3 derivation path was chosen instead.)

    \textbf{O3}~\cite{Beau2026a7}: First quantitative SM connection.
    The phenomenological window $\beta^* \in (0.09, 0.13)$ is derived from the charged-lepton
    mass ratios $m_e : m_\mu : m_\tau$ (\sstruct).

    \textbf{O4}~\cite{Beau2026a8}: The structural upper bound $\beta \leq 1$ follows from the
    BI flux constraint and the Cheeger isoperimetric inequality (\sproved).

    \textbf{O5}~\cite{Beau2026a9}: Obstruction theorem.
    The $\beta$~gap cannot be closed by any purely representation-theoretic or
    fixed-representation approach (\sproved).

    \textbf{O6}~\cite{Beau2026a10}: Matrix-level confinement of the cascade exponent (\sproved).

    \textbf{O7}~\cite{Beau2026a11}: Reformulates the target as a capacity exponent
    $\delta \in [7.4, 10.6]$ on three-step path fingerprints (\sstruct).

    \textbf{O8}~\cite{Beau2026a12}: Establishes the geometric obstruction closing the LPS phase.
    Exponential shell growth $|S_n| \sim p^n$ on LPS graphs compresses the
    pre-saturation window to $O(\log q)$ BFS steps (\sproved).

  \subsection{O9--O15: Heisenberg Transition}

    The geometric obstruction identified in O8 motivates replacing LPS graphs by Cayley graphs of
    $\Heis_3(\mathbb{Z}/q\mathbb{Z})$.

    \textbf{O9}~\cite{Beau2026a13}: Structural transition.
    Polynomial ball growth $|B_n| \sim n^4$ provides $\Theta(q)$ usable BFS steps (\sproved).
    This is the key structural transition of the O-series.

    \textbf{O10}~\cite{Beau2026a14}: First large-$q$ computation ($q=101$).
    Confirms $n^4$ growth; a TensorSketch representation obstruction is identified at large~$q$ (\sproved).

    \textbf{O11}~\cite{Beau2026a15}: Bidimensional Fourier-character proxy overcomes the
    TensorSketch obstruction (\sstruct).

    \textbf{O12}~\cite{Beau2026a16}: Exact Weil-block fingerprints resolve the final obstruction.
    Establishes $\hat\delta_{\mathrm{exact}} \approx 4.3$--$4.8$ for $q \in \{29, 61, 101, 151, 211\}$ (\sproved).

    \textbf{O13}~\cite{Beau2026a17}: $\hat\delta_{\mathrm{exact}}(q)$ decreases monotonically from 4.80
    to 3.59; the finite-size hypothesis is definitively refuted (\sproved).

    \textbf{O14}~\cite{Beau2026a18}: Corrects the $\delta \mapsto \beta^*$ relation via block
    normalisation and central-phase contributions (\sstruct).

    \textbf{O15}~\cite{Beau2026a19}: Block-level no-go.
    No reweighting of individual block data can raise $\hat\delta_{\mathrm{exact}}$ to
    $\delta \in [7.4, 10.6]$ (Corollary~4.8, \sproved).
    This result forces the pair observable introduced in O16.

  \subsection{O16--O24: Pair Observable and Unconditional Transfer Chain}

    \textbf{O16}~\cite{Beau2026a20}: Identifies the misidentification of the observable.
    The physically relevant quantity is $\sigma_{\mathrm{pair}}(n) = \sigma_c(n)\cdot\sigma_{q-c}(n)$
    on conjugate pairs $\{c, q-c\}$.
    The exponent doubling $\delta_{\mathrm{pair}} = 2\delta_c \approx 7.44$ resolves the gap (\sstruct).

    \textbf{O17}~\cite{Beau2026a21}: Structural derivation.
    $\rho_{q-c} = \bar\rho_c$ is forced by fibre-level admissibility;
    the pair structure is derived, not postulated (\sproved).

    \textbf{O18}~\cite{Beau2026a22}: Foundational derivation of the parity involution $c \leftrightarrow q-c$.
    BI parity is the only global symmetry of $S_{\mathrm{BI}}[\chi]$, ensuring each fibre of~$\Pi$ is
    exactly $\{\chi, -\chi\}$ (minimal fibre condition, \sproved, Theorem~4.1).

    \textbf{O19}~\cite{Beau2026a23}: The residual amplitude factor $r(c,q) \in \{1,2,3,4\}$ does not
    affect $\delta_{\mathrm{pair}}$; the observable is pipeline-independent (\sproved).

    \textbf{O20}~\cite{Beau2026a24}: Dynamical selection criterion for admissible modes via
    projective persistence (\sstruct).

    \textbf{O21}~\cite{Beau2026a25}: Defines the observable saturation rank $n_3^{\mathrm{obs}}$ via
    $\Sigma_c(n_3) = 3$ and constructs the transfer $\delta_{\mathrm{pair}} \to \beta^*$ (\sstruct).

    \textbf{O22}~\cite{Beau2026a26}: BI projection locking forces $n_3^{\mathrm{obs}}$ onto a BFS
    shell (Theorem~3.2, \sproved).

    \textbf{O23}~\cite{Beau2026a27}: The threshold $\Sigma_c(n_3) = 3$ follows from the quaternionic
    maximality of the admissible neutral generating set (\sproved).

    \textbf{O24}~\cite{Beau2026a28}: Capstone of the analytical O-series.
    The Verticality Lemma (``$\ker\Pi$ is free, $\mathrm{Im}\,\Pi$ is constrained'') closes the
    unconditional transfer chain $c_\chi \to \delta_{\mathrm{pair}} \to \beta^*$
    (Corollary~4.2: $\beta^* \approx 0.126$, \sproved).

  \subsection{O25--O30 and PTO: Numerical Validation, Sector Identification, and Eigenvalue Ratio}

    \textbf{O25}~\cite{Beau2026a29}: Systematic pair-level numerical campaign.
    Computes $\delta_{\mathrm{pair}}$ across all $(q-1)/2$ conjugate pairs with $M=50$ independent
    block samples per pair, for $q \in \{29, 61, 101, 151, 211\}$.
    Results: $\bar\delta_{\mathrm{pair}} \in \{8.89, 9.98, 9.55, 9.13, 8.78\}$ with inter-pair standard
    deviation decreasing from 0.54 to 0.11, confirming $\delta_{\mathrm{pair}}$ as a structural invariant.
    After the O14 normalisation correction, corrected values $\delta_{\mathrm{corr}}(q) \in [7.7, 9.0]$
    fall consistently within the admissible window $[7.4, 10.6]$ for $q \in \{61, 101, 151, 211\}$.
    Direct extrapolation to $q \to \infty$ is shown to be structurally degenerate;
    the central open direction is the analytical control of $n_1(q)/q$ (\sstruct).

    \textbf{O26}~\cite{Beau2026a30}: Dictionary between conjugate Weil blocks and rank-1 matrices in
    $M_2(\mathbb{C})$, connecting the Heisenberg fibre to $2I \subset \SU(2)$ (\sstruct).

    \textbf{O27}~\cite{Beau2026a31}: Every admissible morphism $\Phi_{q,\rho}$ satisfying involution
    equivariance, quadratic compatibility, and naturality factors through $\mathfrak{su}(2)$ (\sproved).

    \textbf{O28}~\cite{Beau2026a32}: Two measurements from the Q5a-O5 checkpoints.
    Part~A: the BFS window ratio $n_1(q)/q$ decreases from 0.138 to 0.066 over
    $q \in \{29, 61, 101, 151, 211\}$ (Scenario~S2, pre-asymptotic regime); OLS fit
    $n_1(q) = \hat\alpha\,q + \hat\beta$ gives $\hat\alpha \approx 0.053$;
    $\delta_{\mathrm{corr}}(q) \in [7.4, 10.6]$ for all tested primes, confirming O25.
    Part~B: formal effective-dimension computation of O26 Criterion~5.4 in
    $\mathrm{End}(H_{\mathrm{eff}})$, $H_{\mathrm{eff}} = \mathbb{C}^3$
    ($\mathrm{HEFF\_DIM} = 3$, consistent with $\Sigma_c(n_3) = 3$ from O23).
    The covariance $\mathcal{C}_c$ has rank exactly~$3$ for every conjugate pair and every
    $q \in \{61, 101, 151\}$ (100\% of pairs), with invariant eigenvalue structure
    $[\lambda_1 : \lambda_2 : \lambda_3] = [1 : \tfrac{1}{2} : \tfrac{1}{2}]$.
    The exact degeneracy $\lambda_2 = \lambda_3$ is a structural consequence of the
    Born--Infeld parity involution $c \leftrightarrow q-c$ (O18), which correlates conjugate
    projections and constrains $\mathcal{C}_c$ to a symmetric subspace.
    The gap from $d_\rho^2 = 4$ reflects $H_{\mathrm{eff}} \neq V_\rho$;
    analysis of $V_\rho \subset H_{\mathrm{eff}}$ is carried out in O29.

    \textbf{O29}~\cite{Beau2026a33}: Spin-$\tfrac{1}{2}$ sector identification via the
    symmetric rank formula (\sstruct, numerically confirmed).
    The Born--Infeld parity constraint $\pi_{q-c}(v) = \overline{\pi_c(v)}$ (O18) is proved to force
    every outer product $M_j = \pi_c(v_j) \otimes \pi_{q-c}(v_j)^*$ into the complex symmetric
    subspace $\mathrm{Sym}(V_\rho, \mathbb{C}) \subset \mathrm{End}(H_{\mathrm{eff}})$.
    This is an algebraic identity, not lifted by any complex-linear reparametrisation.
    The resulting covariance rank satisfies the \emph{symmetric rank formula}
    $r_{\mathrm{eff}} = d_\rho(d_\rho+1)/2$, whose unique positive integer inversion at
    $r_{\mathrm{eff}} = 3$ gives $d_\rho = 2$, confirming the spin-$\tfrac{1}{2}$ sector.
    Numerically: $r_{\mathrm{eff}} = 3$ universally for $q = 61$ (30/30 pairs) and
    $q = 151$ (75/75 pairs) with zero inter-pair variance;
    at $q = 211$ (105/105 pairs, $100\%$, multi-sample confirmed), $r_{\mathrm{eff}} = 3$
    holds universally (the 2 single-sample anomalies confirmed as artefacts);
    at $q = 101$, modal $r_{\mathrm{eff}} = 3$
    is confirmed by a dedicated multi-sample analysis ($M = 5$ resamples per anomalous pair,
    $76.7\%$ of (pair, sample) cells satisfy $r_{\mathrm{eff}} = 3$, with modal $r_{\mathrm{eff}}=3$
    for all $18$ pairs), confirming $d_\rho=2$ at the modal level.
    The O26 Criterion~5.4 is reformulated for conjugate-pair data:
    $d_\rho^2 = 4 \to d_\rho(d_\rho+1)/2$; spin-$\tfrac{1}{2}$ satisfies the
    reformulated criterion exactly.

    \textbf{O30}~\cite{Beau2026a34}: Analytical derivation of the eigenvalue ratio
    $\lambda_1/\lambda_2 = 2$ (\sproved).
    The Born--Infeld parity anti-linearity $\rho_{q-c} = \bar\rho_c$ forces every admissible
    trajectory vector $w_j = \pi_c(v_j) \in V_\rho \cong \mathbb{C}^2$ to satisfy
    $|\alpha_j| = |\beta_j|$ (equatorial constraint), i.e., $w_j$ lives on an
    equatorial $S^1 \subset S^3$ in $V_\rho$.
    In the equatorial regime, the central component $\sqrt{2}\,\alpha_j\beta_j$ of
    $\operatorname{vec}(M_j)$ is phase-independent (the phases cancel exactly), while the
    diagonal components $\alpha_j^2$ and $\beta_j^2$ oscillate as $e^{\pm 2i\phi_j}$.
    The covariance then diagonalises under the single-harmonic phase decorrelation condition
    $\langle e^{2i\phi_j}\rangle = 0$, yielding
    $\mathcal{C}_c = \langle r_j^4\rangle \cdot \mathrm{diag}(1/4, 1/2, 1/4)$
    and spectral ratio $[1:\tfrac{1}{2}:\tfrac{1}{2}]$ exactly.
    The factor of~$2$ is purely structural: it is the squared symmetric-tensor normalisation
    coefficient in $e_0 = (v_+\!\otimes v_- + v_-\!\otimes v_+)/\sqrt{2}$, isolated by the
    equatorial constraint as the sole source of eigenvalue asymmetry.
    The correction to the equatorial condition is $O(q^{-1/2})$ from U1~\cite{Beau2026u1}.
    This closes the open direction of O28--O29 \S7.4.

    \textbf{O31}~\cite{Beau2026a35}: Structural framework for the SU(3) identification (\sstruct).
    Shows the O23 Hurwitz argument cannot directly produce $d_\rho = 3$ (proved).
    Defines the \emph{colour triplet} $\{c_1,c_2,c_3\} \subset (\mathbb{Z}/q\mathbb{Z})^*$
    with $c_1+c_2+c_3 \equiv 0 \pmod{q}$; such triplets exist iff $q \equiv 1 \pmod{3}$ (proved).
    The metaplectic automorphism $\phi_\omega(a,b,z) = (\omega a, \omega^{-1}b, z)$
    forces $\sigma_c(n) = \sigma_{\omega c}(n)$ for all shells on the colour-adapted Cayley
    graph $\mathrm{Cay}(G_q, \mathcal{S}_q^{(3)})$ (proved, Theorem~4.4).
    Conditional on Hypothesis~[H-color] (triplet co-admissibility for the standard graph),
    the symmetry group of the co-admissible triplet is exactly $\SU(3)$, with
    $\mathrm{U}(3)$, $\mathrm{SO}(3)$, $\mathrm{U}(2)$, $G_2$ excluded (proved).
    The Standard Model gauge group $G_{\mathrm{SM}} = \SU(3)\times\SU(2)\times\mathrm{U}(1)$
    follows as a composite of three admissibility fixed points (proved for $\mathcal{S}_q^{(3)}$;
    conditional on [H-color] for $\mathcal{S}_q$).
    U1 universality implies $|\sigma_c - \sigma_{\omega c}| = O(q^{-1/2})$ for any generating
    set, so the identification is generating-set-independent in the large-$q$ limit.
    The generating-set independence operates at two levels (\emph{two-tier result}):
    (i)~exactly, for the colour-adapted graph $\mathrm{Cay}(G_q, \mathcal{S}_q^{(3)})$
    (metaplectic argument, Theorem~4.4);
    (ii)~up to $O(q^{-1/2})$, for \emph{any} generating set including $\mathcal{S}_q$
    (U1 universality, Proposition~4.7).
    Proposition~4.6 shows that $\mathcal{S}_q^{(3)}$ is the \emph{canonical} colour-sector
    generating set: the minimal extension of $\mathcal{S}_q$ closed under $\phi_\omega$,
    in exact analogy with $\mathcal{S}_q$ being canonical for the pair sector under $\phi_{-1}$.
    Additionally, Theorem~5.3 (\emph{generator-twist isospectrality}) proves that the
    Weil-sector Markov operator is isospectral under the generator twist
    $\mathcal{S}_q \mapsto \phi_\omega(\mathcal{S}_q)$:
    $\operatorname{spec}(\rho_c(P_{\mathcal{S}_q})) = \operatorname{spec}(\rho_c(P_{\phi_\omega(\mathcal{S}_q)}))$
    for all $c \in (\mathbb{Z}/q\mathbb{Z})^*$, confirmed to machine precision
    ($|\Delta\lambda| < 10^{-12}$) for all $q \equiv 1\pmod{3}$, $q \leq 157$.
    However, this isospectrality does \emph{not} extend across distinct central characters:
    $\operatorname{spec}(\rho_c(P_{\mathcal{S}_q})) \neq
    \operatorname{spec}(\rho_{\omega c}(P_{\mathcal{S}_q}))$ in general
    ($\max|\Delta\lambda| \approx 0.3$--$0.4$), establishing that [H-color] on the standard graph
    cannot be proved through global Markov-spectrum equality; the BFS capacity is a strictly
    finer observable.
    The correct algebraic mechanism is identified by two new results.
    \emph{Intra-coset Vandermonde symmetry} (Lemma, proved):
    the irreducibility of the Weil representation (Schur's lemma) forces the Heisenberg centre
    to act as a scalar in each $\rho_{c_i}$, so every horizontal coset $(a,b)$ contributes
    exactly one independent direction to each colour summand $V_{c_i}$;
    the Vandermonde invertibility of the triplet phase matrix $(\lambda_j^k)_{j,k}$, with
    $\lambda_j = e^{2\pi i c_j/q}$, then guarantees this, independently of any spectral property
    of $\rho_c(P_{\mathcal{S}_q})$.
    \emph{Colour sector rank equality} (Proposition, proved unconditionally):
    $r_c(n) = r_{\omega c}(n) = r_{\omega^2 c}(n)$ for all BFS depths~$n$ and any seed,
    unconditionally on the standard graph.
    This proves [H-color] at the level of BFS sector ranks without reference to the global Markov
    spectrum; whether the full O12/O32 capacity functional $\sigma_c(n)$ inherits this equality
    is addressed numerically by~O32.
    Section~6 provides the conceptual unification: $\mathrm{U}(1)$, $\SU(2)$, $\SU(3)$ arise
    from BI-admissible fibre orbits of size~$1$, $2$, $3$ respectively (phase non-injectivity,
    minimal correlated non-injectivity, relational correlated non-injectivity), with
    non-factorisability (Foundation~M, Axiom~A3) as the uniform structural origin.
    \textbf{O32}~\cite{Beau2026a36}: tests [H-color] numerically on
    $q\in\{61,151,211\}$ (test, $q\equiv 1\pmod{3}$) and $q\in\{29,101\}$ (controls).
    Combined noise floor $\mathtt{ctrl\_ref} = 3.81\times10^{-3}$.
    Normalised ratios: $R = 0.90$ ($q=61$, 1/4 triplets valid),
    $R = 0.19$ ($q=151$, 4/4 triplets), $R = 0.42$ ($q=211$, 4/4 triplets).
    All three pass $R \leq 3$; $\delta_{\mathrm{tri}} \approx 3\delta_c$ at sub-percent level;
    $C_{\mathrm{color}}$ has numerical rank~1 in all cases.
    $q = 307$: in progress.
    Additionally proves analytically (Proposition~avg-hcolor) that
    $\mathbb{E}[\sigma_c(n)] = \mathbb{E}[\sigma_{\omega c}(n)] + O(q^{-1})$,
    establishing $\Hcolor_{\mathrm{eff}}$ (capacity-exponent equality) in the $q\to\infty$
    limit; the observed $R_{\mathrm{var}} \propto q^{-1}$ decrease is the predicted
    modulation bias.
    Status: \sstruct{} ([H-color] numerically confirmed for $q\in\{151,211\}$;
    $\Hcolor_{\mathrm{eff}}$ analytically established; pointwise proof open).

    \textbf{PTO}~\cite{Beau2026pto}: The cumulative projected capacity
    $I(n) = \sigma_{\mathrm{pair}}(0) - \sigma_{\mathrm{pair}}(n)$ is strictly non-decreasing and
    hence compatible with an arrow of time.
    Confirmed numerically for $q \in \{29, 61, 101, 151, 211\}$ (\sstruct).
    The admissible cascade is shown to carry the structure of an oriented state machine:
    nodes are admissible projections, edges are admissible transitions, and branching weights
    play the role of quantum probabilities.
    The first transition $U_0 \to U_1$ is guaranteed by projective incompleteness
    (Foundation Corollary to Theorem~5.4): temporal ordering starts as a structural necessity,
    not a postulate.
    Open: whether the characteristic shell $n^*(q)$ coincides with the locking depth $n_c(q)$
    at which BFS coverage transitions from locally to universally dominated — which would connect
    the spectral ordering to the effective geometry results of Q10~\cite{Beau2026q10}.

  \section{Branch III: Q-Series and Physical Applications}
  \label{sec:qseries}

  \subsection{Q-Series: Quantum Mechanics and Spacetime Emergence}

    The Q-series derives quantum-mechanical and geometric structure from the Foundation axioms,
    taking as input the fibre identification $F_n \cong V_\rho$ and selected O-series results.

    \textbf{Q1}~\cite{Beau2026q1}: Phase coherence is a structural consequence of projective admissibility (not a
    postulate).
    Theorem~2.7 proves that any admissible transition preserves the BI indiscernibility of conjugate
    Weil blocks $\rho_c$ and $\rho_{q-c}$, maintaining the metaplectic phase coherence of the fibre.
    The singlet correlator $E(\hat{a},\hat{b}) = -\hat{a}\cdot\hat{b}$ and the Tsirelson bound
    are derived from admissibility, O18, and O23 (\sproved; numerically validated for $q=29$).

    \textbf{Q2}~\cite{Beau2026q2}: Extends the programme to spin-$\tfrac{3}{2}$.
    On the binary icosahedral group~$2I$, the spin-$\tfrac{1}{2}$ and spin-$\tfrac{3}{2}$ sectors
    share the Laplacian eigenvalue $\lambda_{1/2} = \lambda_{3/2} = 18$ (co-admissibility).
    The Born rule, singlet correlator, and Tsirelson bound are derived for spin-$\tfrac{3}{2}$
    without new postulates.
    $\SU(2)$ is established as the stable fixed point of the admissibility flow (\sproved{} for
    spin-$\tfrac{3}{2}$; general-$j$ extension proved in Q3~\cite{Beau2026q3}).

    \textbf{Q3}~\cite{Beau2026q3}: Completes the $\SU(2)$ quantum sector for all admissible~$j$.
    BI indiscernibility forces the bipartite proto-state to be invariant under the diagonal
    $2I$-action on $V_{\chi_{2j+1}}\otimes V_{\chi_{2j+1}}$; Schur's lemma applied to the
    Clebsch--Gordan decomposition $\chi_{2j+1}\otimes\chi_{2j+1} = \bigoplus_{J=0}^{2j}\chi_{2J+1}$
    uniquely identifies the proto-state as the singlet $|\Omega_j\rangle$.
    The universal correlator $E(\hat{a},\hat{b}) = -j(j+1)/3\cdot(\hat{a}\cdot\hat{b})$ and the Born
    rule are derived for all five admissible sectors
    $j \in \{\tfrac{1}{2}, 1, \tfrac{3}{2}, 2, \tfrac{5}{2}\}$ of~$2I$ (\sproved).
    Closes the open step of~Q2 (identification of the isotropic fibre state with the
    proto-state for spin-$\tfrac{3}{2}$, and general-$j$ extension).

    \textbf{Q5a}~\cite{Beau2026q5a}: Under Mosco hypotheses, the admissibility forms~$\mathcal{E}_q$
    on $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ converge to $L_\Pi = -A\partial_x^2$ on $L^2(\mathbb{R})$
    (\sstruct, conditional).

    \textbf{Q5b}~\cite{Beau2026q5b}: The BFS shell stratification of $\Heis_3(\mathbb{R})$
    produces a four-dimensional Lorentzian spacetime, with the temporal direction identified
    with the BFS depth.
    Hypothesis~[H-lift] (Q5b-O1), formerly conditional, is proved by Q9~\cite{Beau2026q9}
    (\sstruct; unconditional with respect to~[H-lift] via Q9).

    \textbf{Q6a}~\cite{Beau2026q6a}: Gauge charges are the invariants of the projection-fibre
    equivalence classes.
    $\mathrm{U}(1)$ and $\SU(2)$ are identified as fixed points of the admissibility flow.
    $\SU(3)\times\SU(2)\times\mathrm{U}(1)$ is derived as a composite (\sstruct; $\SU(3)$:
    conditional on [H-color], see O31~\cite{Beau2026a35}).

    \textbf{Q6b}~\cite{Beau2026q6b}: Effective Lorentzian geometry from the admissibility filter
    $\Pi_q$; inherits Q5a hypotheses only ([H-lift] closed by Q9).
    Derives the effective metric $g^{\mu\nu}(x) \propto A^{\mu\nu}(x)$ of Lorentzian signature
    $(-,+,+,+)$ from the principal symbol of $\mathcal{L}_{\mathrm{eff}}$; with Q8, Q10, Q11 the
    co-metric is fully explicit: $g^{\mu\nu} = \mathrm{diag}(-2,2,2,2)$.
    Proves the Schwarzschild metric as the unique stationary exterior solution under spherical
    symmetry and flux conservation; the horizon appears as a principal-symbol degeneracy.
    Establishes the Hamilton--Jacobi equation $g^{\mu\nu}\partial_\mu S\,\partial_\nu S=0$ as the
    effective massless propagation structure.
    The Einstein equations emerge as consistency conditions via the spectral entropy functional.
    Closes the geometric chain
    $\Pi_q \xrightarrow{\text{Q5a}} \mathcal{L}_\Pi \xrightarrow{\text{Q5b}} g^{\mu\nu}
    \xrightarrow{\text{Gravity}} G_{\mu\nu}$
    (\sstruct, conditional on Q5a).

    \textbf{Q7}~\cite{Beau2026q7}: Bridge candidate between the admissible dimension
    $\dim H_{\mathrm{eff}} = 3$ (O23--O29) and the three spatial dimensions of Q5b.
    Proves $[\mathrm{su}(2)] \not\cong \mathrm{heis}_3$ (the bridge cannot be a Lie algebra
    isomorphism) and identifies $H_{\mathrm{eff}} \cong \mathrm{Sym}^2(V_\rho)$ as the spin-1
    representation of $\mathrm{su}(2)$ (O29).
    Establishes structural uniqueness of the bridge via Schur's lemma, and reduces the
    identification to the isotropy condition $A_H = A_z$ on $\sigma_2(L_{\mathrm{eff}})$.
    Proves analytically $[F_c, L_{\mathrm{Weil}}] = 0$, which forces the cross terms
    $k_X k_Z = k_Y k_Z = 0$ structurally.
    Numerical evidence on O25 checkpoints ($q \in \{61,101,151,211\}$) gives
    $A_z = 2$ universally and $|A_H - A_z| \to 0$; four-point OLS fit gives
    $|A_H - A_z| \approx 0.364\,q^{-0.52}$ ($R^2=0.98$), consistent with $O(q^{-1/2})$
    (Q5b Theorem~3.2).
    (\sstruct; asymptotic isotropy $A_H \to 2 = A_Z$ proved by Q10 and U1, conditionally on~[U];
    bridge existence at finite~$q$: \sopen).

    \textbf{Q8--Q11, U1, W1, H2 (Geometric emergence cluster).}
    Q8~\cite{BeauQ8} establishes $A_Z = C_{\mathfrak{su}(2)} = 2$ unconditionally under Q5a
    via Casimir rigidity (\sstruct).
    Q9~\cite{Beau2026q9} proves [H-lift] as a theorem: the modulation generator is suppressed at
    rate $O(q^{-1/2})$, and $A_H > 0$ follows by coercivity independently of the bridge (\sproved,
    under Q5a).
    Q10~\cite{Beau2026q10} proves $A_H \to 2$ under spectral universality~[U]:
    character-independence forces $\mathfrak{su}(2)$-isotropy of the effective form,
    and the unique such form is the Casimir with value~2 (\sstruct, conditional on [U]).
    U1~\cite{Beau2026u1} proves [U] with rate $\varepsilon(q) = O(q^{-1/2})$ from the Weil-generator
    Lipschitz bound and BFS--Carnot--Carathéodory convergence (\sproved{}).
    W1~\cite{Beau2026w1} proves Hypothesis~[H-w] (convergence $a_q(s) \to A > 0$ of the
    admissibility weights) as a structural consequence of the fibre-invariance of admissible
    observables ($\mathcal{O} = \mathrm{Im}\,\Pi$), made quantitative by U1 (\sproved{}).
    After W1, the open Q5a hypotheses reduce to three: [H1], [H-E1], and [C].
    Q5a-O2~\cite{Beau2026q5ao2} subsequently proves that [H1] is not needed in full generality on the admissible sector,
    and closes [H-E1] and [C] via spectral atomicity.
    H2~\cite{Beau2026h2} proves the last open hypothesis, [H2] (strong convergence of the rescaled
    Weil generators $\hat{X}_q \to x$ and $\hat{P}_q \to -i\partial_x$), via a quantitative
    Poisson aliasing lemma and a discrete Sobolev identity (\sproved{}).
    All hypotheses of the Q5a large-$q$ convergence theorem are verified unconditionally
    on the admissible sector.
    \textbf{Q11}~\cite{Beau2026q11}: Temporal Casimir rigidity closes Q5b open problem~O3
    (identification of $A_\tau$ from admissibility data) (\sstruct).
    The cascade increment operator internalises no new irreducible representation
    (Schur rigidity); asymptotic $\mathfrak{su}(2)$-equivariance forces the temporal
    coefficient $A_\tau = 2$, identical to the spatial Casimir value.
    The effective Lorentzian co-metric is thereby fully identified:
    $g^{\mu\nu} = \mathrm{diag}(-2, 2, 2, 2) \propto \eta^{\mu\nu}$ (Minkowski).
    The derivation chain Q5a $\to$ Q5b $\to$ Q7 $\to$ Q8 $\to$ Q9 $\to$ Q10 $\to$
    U1 $\to$ W1 $\to$ H2 $\to$ Q11 $\to$ Q5b-O3 closed is now complete.

    \textbf{Q12}~\cite{Beau2026q12}: Yang--Mills dynamics from the vertical variation of
    the projective spectral entropy (\sstruct, conditional on Q6a for the gauge group;
    $\SU(3)$ sector inherits [H-color] conditionality from~\cite{Beau2026q6a,Beau2026a35}).
    The Gravity paper~\cite{Beau2026h} derived the Einstein tensor as the infrared-dominant
    horizontal response of $S_\Pi[g] = \tfrac{1}{2}\log\det' A_g$ (the $a_2$ coefficient).
    Q12 carries out the complementary vertical variation: the operator $A_g$ is extended to
    $A_{g,\mathcal{A}} = -(\nabla^\mathcal{A})^2 + E$ on the associated vector bundle of the
    admissible principal bundle $P_{G_\Pi}(M, G_\Pi)$, and the Seeley--DeWitt coefficient $a_4$
    is computed:
    \[
      a_4(A_{g,\mathcal{A}})\big|_{\mathrm{gauge}}
      = \frac{1}{16\pi^2}\int \frac{1}{12}\,\mathrm{Tr}(F_{\mu\nu}F^{\mu\nu})
        \sqrt{g}\,\mathrm{d}^4 x\,.
    \]
    The extended spectral entropy $S_\Pi[g,\mathcal{A}]$ therefore contains the renormalized
    Yang--Mills term with logarithmic coupling $g_{\mathrm{YM}}^{-2}
    \sim (12\cdot 16\pi^2)^{-1}\log(\Lambda/\mu)$,
    and the vertical variation $\delta_\mathcal{A}S_\Pi = 0$ yields the Yang--Mills equations
    $D_\mu F^{a\mu\nu} = 0$ in the current-free sector (\sproved{} for the $a_4$ derivation
    given $G_\Pi$).
    The induced Newton's constant $G_N^{-1} \sim \ell_{\mathrm{sp}}^{-2}$ (quadratic UV)
    and the induced gauge coupling (logarithmic UV) share the same spectral cutoff
    $\ell_{\mathrm{sp}}$; the gauge--gravity hierarchy $G_N g_{\mathrm{YM}}^2 \ll 1$ is a
    structural consequence of the Seeley--DeWitt expansion and requires no fine-tuning.
    The horizontal--vertical decoupling lemma guarantees that the Einstein and Yang--Mills
    sectors are independent at orders $a_2$ and~$a_4$: $a_2 \to \text{Einstein}$,
    $a_4 \to \text{Yang--Mills}$, from the single functional $S_\Pi[g,\mathcal{A}]$.
    Beyond the technical derivation, Q12 identifies a conceptual principle:
    gravity and gauge dynamics are separated by geometric direction (horizontal
    vs.\ vertical variation on the admissible bundle) \emph{and} by spectral order
    in the Seeley--DeWitt hierarchy, not by a missing symmetry group.
    The distinct UV behaviours --- quadratic divergence for gravity, logarithmic
    for gauge --- are structural consequences of this spectral stratification
    and require no independent input.
    This suggests that the natural organisational space for unification in the
    present framework is spectral and variational rather than primarily
    group-theoretic: the difficulty of reconciling gravity with the gauge-theoretic
    Standard Model may reflect a difference of Seeley--DeWitt order rather than
    the absence of a common symmetry group~$G_{\mathrm{unif}}$.
    The gauge--gravity synthesis is carried out in Q13.

    \textbf{Q13}~\cite{Beau2026q13}: Gauge--gravity spectral synthesis (\sstruct, conditional
    on Q12 and the Gravity paper; SU(3) sector inherits [H-color] conditionality).
    Q13 completes the trilogy (Gravity, Q12, Q13) by solving the \emph{joint} variational
    problem $\delta_{g,\mathcal{A}} S_\Pi = 0$ and deriving the coupled Einstein--Yang--Mills
    system.
    The metric variation of the $a_4$ coefficient yields the Yang--Mills stress tensor as the
    source term for gravity: $G_{\mu\nu} = 8\pi G_N T^{YM}_{\mu\nu} + \mathcal{O}(a_6)$
    (\sproved{} modulo the Lemma on metric-independence of $F_{\mu\nu}$).
    The $a_6$ Seeley--DeWitt coefficient is computed and produces the leading gauge--gravity
    cross-coupling $R_{\mu\nu\rho\sigma}F^{\mu\nu}F^{\rho\sigma}$, suppressed by
    $\ell_{\mathrm{sp}}^2$ (\sstruct).
    The Eddington--Born--Infeld completion of the joint functional is constructed from the
    same $c_\chi$ saturation bound, recovering both sector-specific BI completions as limits
    (\sstruct, with residual ambiguity in the tensor $\Xi_{\mu\nu}$).
    The gauge--gravity hierarchy is a structural output:
    \[
      G_N g_{\mathrm{YM}}^2
      \;\sim\;
      \frac{\ell_{\mathrm{sp}}^2}{\dim V}\cdot\Bigl[\log\frac{\Lambda}{\mu}\Bigr]^{-1}
      \;\ll\; 1,
    \]
    without fine-tuning, as a direct consequence of the Seeley--DeWitt stratification
    ($a_2 \to$ gravity at quadratic UV, $a_4 \to$ gauge at logarithmic UV).
    The central conceptual contribution is the identification of the spectral stratification
    principle: gravity and gauge dynamics are not unified by enlarging the symmetry group,
    but are \emph{stratified by Seeley--DeWitt order} within the single operator
    $\mathcal{A}_{g,\mathcal{A}}$.
    The fermionic extension is carried out in Q14.

    \textbf{Q14}~\cite{Beau2026q14}: Fermionic matter and chirality (\sstruct, conditional
    on Q13, the Gravity paper, and the BI paper; colour sector inherits [H-color] conditionality).
    Q14 extends the gauge--gravity synthesis to the fermionic sector.
    Fermions are not postulated as external fields: they arise as the spinorial face of the
    Weil module $V_\rho$ already forced by non-injective admissibility, once its metaplectic
    Lie-algebraic structure is complexified by the Lorentzian metric.
    Three structural results are proved.
    (i)~The admissible Weil module induces, through its metaplectic lift and the complexification
    $\mathfrak{mp}(2,\mathbb{R})_{\mathbb{C}} \simeq \mathfrak{sl}_2(\mathbb{C})$, an admissible
    spinor bundle $S_\Pi$ whose symmetric and determinant tensor sectors reproduce the
    $\SU(2)_L \times U(1)_Y$ electroweak bundle structure (\sstruct).
    (ii)~The projected Dirac operator $\mathcal{D}_{\Pi,g,A}$ contains a canonical zero-order
    endomorphism $E_\Pi$ (the internal spectral residue of non-injective projection) which,
    under the spinorial lift of BI parity, is left-admissible and enforces the $V{-}A$ chiral
    structure; the $\gamma_5$-weighted $a_4$ Seeley--DeWitt coefficient then imposes
    anomaly-cancellation trace constraints on the hypercharge weights, making hypercharge
    a spectral coherence datum rather than a free parameter (\sstruct).
    (iii)~The saturation invariant $\sigma_c(n_3) = 3$ admits a spinorial multiplicity reading,
    distinct from its geometric reading as three spatial directions, yielding a gauge-singlet
    three-generation factor
    $\mathbb{C}^3_{\mathrm{gen}} \subset \ker(\operatorname{ad}_{\SU(2)} \oplus Y)$ (\sstruct).
    The colour-coupled quark sector follows by tensoring with $V_{\mathrm{color}}$,
    conditional on [H-color].

  \subsection{Gravity and Spacetime Track}

    \textbf{Spectral2}~\cite{Beau2026a}: Derives operational metric distances from graph Laplacians
    on a relational substrate without any background manifold (\sstruct).

    \textbf{Gravity}~\cite{Beau2026h}: Derives $G_{\mu\nu} = 8\pi G_N T^{(\Pi)}_{\mu\nu}$ from the
    metric variation of $S_\Pi[g] = \tfrac{1}{2}\log\det' A_g$, via heat-kernel and zeta
    regularisation (\sproved{} at leading IR order). Establishes that the UV completion is uniquely
    determined to be of determinantal Born--Infeld form
    $\sqrt{-\det(g_{\mu\nu}+\ell_{\mathrm{sp}}^2 R_{\mu\nu})}-\sqrt{-g}$,
    with Einstein gravity as the universal two-derivative IR sector (\sproved).

    \textbf{Thermodynamics}~\cite{Beau2026Thermodynamics}: Develops a local thermodynamic interpretation.
    The diagonal heat kernel yields a local multiplier field
    $\beta(x)^{-1} = \beta_0^{-1} - \tfrac{1}{6}R(x) + O(\nabla^2 R)$, and a spectral first law
    $\delta S_\Pi = \int \beta(x)^{-1}\,\delta E_\Pi(x)$ recasts the Einstein equation as a
    spectral equilibrium condition (\sstruct; Lorentzian extension and matter coupling: \sopen).

    \textbf{Lorentz}~\cite{Beau2026i}: Lorentzian completion of the spectral action.
    Causal propagation and gravitational wave propagation follow from the hyperbolic continuation
    (\sproved{} for the Lorentzian extension; GW spectrum: \sstruct).

  \subsection{Standard Model Companion Papers}

    \textbf{BornInfeld}~\cite{Beau2026c}: BI action as the unique minimal local representation
    consistent with a universal bound on admissible relational gradients (\sproved).

    \textbf{TopologicalInvariants}~\cite{Beau2026k}: Charge quantisation ($\pi_1(S^1) \cong \mathbb{Z}$)
    and absence of magnetic monopoles from the Hopf fibration $S^1 \hookrightarrow S^3 \to S^2$
    of the projection fibre (\sproved; $\pi_2(\mathcal{C}_{\mathrm{eff}}) = 0$ beyond the canonical model:
    \sopen, Remark~4.2).

    \textbf{SMchargemass}~\cite{Beau2026e}: Mass and electric charge as BI-saturated responses
    (\sstruct; baryon-to-photon ratio~$\eta$: \sopen).

    \textbf{Bell}~\cite{Beau2026b}: Bell-inequality violations from non-injectivity alone, without
    nonlocality or additional hidden variables (\sproved).

    \textbf{SchwingerLamb}~\cite{Beau2026f}: Fine-structure constant~$\alpha$ as a projective invariant;
    Lamb shift and Schwinger correction rederived in the pre-geometric framework
    (\sstruct; quantitative radiative corrections: \sheur).

  \subsection{Cosmological and Condensed-Matter Applications}

    \textbf{Cosmology}~\cite{Beau2026d}: Flat galaxy rotation curves and the Hubble tension from a
    common effective mechanism; no dark matter or modified gravity (\sstruct; quantitative fit: \sheur).

    \textbf{Superconductivity}~\cite{Beau2026g}: Projective phase locking as the structural origin of
    superconducting coherence across BCS, cuprate, and nickelate systems (\sstruct).

  \section{Dependency Structure}
  \label{sec:graph}

  Figure~\ref{fig:dag} presents the logical dependency DAG.
  Three entry paths emerge for external readers.

  \paragraph{Foundational path.}
    $\text{ENI} \to \text{Foundation} \to \text{HeisenbergStructure} \to \text{noscale}$.
    Requires least prior knowledge; establishes the axiomatic core.

  \paragraph{Spectral path.}
    $\text{BornInfeld} \to \text{SpAdm} \to \text{SpRel} \to \text{O1} \to \cdots \to \text{O24} \to \text{O25} \to
    \text{O28} \to \text{O29}$.
    Develops the spectral machinery and the transfer chain.

  \paragraph{Physical path.}
    Foundation $+ $ O18 $+$ O22 $+$ O23 $\to$ Q1 $\to$ Q2 $\to$ Q3; Q2 $\to$ Q5a $\to$ Q5b $\to$ Q6a $+$ Q6b;
    O23 $+$ O28 $+$ O29 $+$ Q5b $\to$ Q7 (dimensional bridge);
    parallel: Spectral2 $\to$ Gravity $\to$ Thermodynamics $\to$ Lorentz.

    \begin{figure}[p]
      \centering
      \resizebox{\textwidth}{!}{%
        \begin{tikzpicture}[
          every node/.style={font=\small\sffamily},
          box/.style={draw, rounded corners=3pt, inner sep=4pt,
          minimum width=1.7cm, minimum height=0.6cm},
          P/.style={box, fill=green!8,  draw=cproved,  text=black},
          S/.style={box, fill=blue!6,   draw=cstruct,  text=black},
          H/.style={box, fill=orange!10,draw=cheur,    text=black},
          Oc/.style={box, fill=red!6,   draw=copen,    text=black},
          arr/.style={-{Stealth[length=4pt,width=3pt]}, gray!60, line width=0.9pt},
          spine/.style={-{Stealth[length=5pt,width=3.5pt]}, black!55, line width=1.4pt},
        ]

\newcommand{\dx}{2.1cm}
\newcommand{\dy}{1.35cm}

\node[P] (WP)     at (0,0)          {WP};
\node[P] (ENI)    at (\dx,0)        {ENI};
\node[P] (Found)  at (2*\dx,0)      {Found};
\node[P] (Heis)   at (3*\dx,0)      {HeisStr};
\node[P] (nos)    at (4*\dx,0)      {noscale};

\draw[spine] (WP)--(ENI);
\draw[spine] (ENI)--(Found);
\draw[spine] (Found)--(Heis);
\draw[arr]   (Found)--(nos);

\node[P]  (BI)    at (0,-\dy)       {BornInfeld};
\node[P]  (SpA)   at (\dx,-\dy)     {SpAdm};
\node[P] (SpCap) at (2*\dx,-\dy)   {SpCap};
\node[P]  (SpG)   at (3*\dx,-\dy)   {SpGram};
\node[S]  (ThGn)  at (4*\dx,-\dy)   {3Gen};
\node[P]  (SpR)   at (\dx,-2*\dy)   {SpRel};

\draw[arr]   (WP)--(BI);
\draw[arr]   (BI)--(SpA);
\draw[arr]   (SpA)--(SpCap);
\draw[arr]   (SpCap)--(SpG);
\draw[arr]   (SpG)--(ThGn);
\draw[spine] (SpA)--(SpR);

\node[P] (O1)  at (0,-3*\dy)        {O1};
\node[S] (O3)  at (\dx,-3*\dy)      {O3};
\node[P] (O4)  at (2*\dx,-3*\dy)    {O4};
\node[P] (O5)  at (3*\dx,-3*\dy)    {O5};
\node[S] (O7)  at (4*\dx,-3*\dy)    {O7};
\node[P] (O8)  at (5*\dx,-3*\dy)    {O8};

\draw[spine] (SpR) to[out=-90,in=90] (O1);
\draw[arr]   (O1)--(O3);
\draw[arr]   (O3)--(O4);
\draw[arr]   (O4)--(O5);
\draw[arr]   (O5)--(O7);
\draw[spine] (O7)--(O8);

\node[P] (O9)   at (0,-4*\dy)       {O9};
\node[P] (O12)  at (\dx,-4*\dy)     {O12};
\node[P] (O13)  at (2*\dx,-4*\dy)   {O13};
\node[P] (O15)  at (3*\dx,-4*\dy)   {O15};

\draw[spine] (O8) to[out=-90,in=90] (O9);
\draw[arr,dashed] (O9) -- node[above,font=\tiny]{O10--O11} (O12);
\draw[arr]   (O12)--(O13);
\draw[spine] (O13)--(O15);

\node[S] (O16)  at (0,-5*\dy)       {O16};
\node[P] (O17)  at (\dx,-5*\dy)     {O17};
\node[P] (O18)  at (2*\dx,-5*\dy)   {O18};
\node[P] (O19)  at (3*\dx,-5*\dy)   {O19};
\node[P] (O22)  at (4*\dx,-5*\dy)   {O22};
\node[P] (O23)  at (5*\dx,-5*\dy)   {O23};
\node[P] (O24)  at (6*\dx,-5*\dy)   {O24};

\draw[spine] (O15) to[out=-90,in=90] (O16);
\draw[arr]   (O16)--(O17);
\draw[spine] (O17)--(O18);
\draw[arr]   (O18)--(O19);
\draw[arr,dashed] (O19) -- node[above,font=\tiny]{O20--O21} (O22);
\draw[arr]   (O22)--(O23);
\draw[spine] (O23)--(O24);

\node[S] (O25)  at (4*\dx,-6*\dy)   {O25};
\node[S] (O26)  at (5*\dx,-6*\dy)   {O26};
\node[P] (O27)  at (6*\dx,-6*\dy)   {O27};
\node[S] (O28)  at (7*\dx,-6*\dy)   {O28};
\node[S] (O29)  at (7*\dx,-7*\dy)   {O29};
\node[P] (O30)  at (7*\dx,-8*\dy)   {O30};
\node[font=\tiny\sffamily,text=cproved,right=2pt] at (O30.east)
  {$\lambda_1/\lambda_2=2$};
\node[S] (O31)  at (7*\dx,-9*\dy)   {O31};
\node[font=\tiny\sffamily,text=cstruct,right=2pt] at (O31.east)
  {SU(3) [H-color]};
\node[S] (O32)  at (7*\dx,-10*\dy)  {O32};
\node[font=\tiny\sffamily,text=cstruct,right=2pt] at (O32.east)
  {$q{=}61,151,211$ pass; 307 prog.};
\node[S] (PTO)  at (5*\dx,-7*\dy)   {PTO};

\draw[spine] (O24) -- (O25);
\draw[arr]   (O24) -- (O26);
\draw[arr]   (O26) -- (O27);
\draw[arr]   (O24) -- (PTO);
\draw[spine] (O25) -- (O28);
\draw[arr]   (O27) -- (O28);
\draw[spine] (O28) -- (O29);
\draw[arr]   (O27) -- (O29);
\draw[spine] (O29) -- (O30);
\draw[spine] (O30) -- (O31);
\draw[spine] (O31) -- (O32);

\node[P] (Q1)   at (8*\dx,-4*\dy)   {Q1};
\node[P] (Q2)   at (8*\dx,-5*\dy)   {Q2};
\node[P] (Q3)   at (9*\dx,-5*\dy)   {Q3};
\node[font=\tiny\sffamily,text=cproved,right=2pt] at (Q3.east)
  {general-$j$ complete};
\node[S] (Q5a)  at (8*\dx,-6*\dy)   {Q5a};
\node[P] (Q5aO2) at (9*\dx,-6*\dy)  {Q5a-O2};
\node[S] (Q5b)  at (8*\dx,-7*\dy)   {Q5b};
\node[S] (Q6a)  at (8*\dx,-8*\dy)   {Q6a};
\node[S] (Q6b)  at (8*\dx,-9*\dy)   {Q6b};
\node[S] (Q7)   at (8*\dx,-10*\dy)  {Q7};
\node[P,dashed,draw=cproved!60,fill=green!4,font=\tiny\sffamily]
(geom)  at (8*\dx,-11*\dy)  {\begin{tabular}{c}
                               Q8--Q10\\U1, W1
\end{tabular}};
\node[P] (H2)   at (9*\dx,-7*\dy)   {H2};
\node[font=\tiny\sffamily,text=cproved,right=2pt] at (H2.east)
  {[H2] proved};

\draw[arr]   (Q5b)   to[out=-30,in=30]  (Q7);
\draw[arr]   (O23)   to[out=-10,in=180] (Q7);
\draw[arr]   (O28)   to[out=-10,in=180] (Q7);
\draw[arr]   (O29)   to[out=-10,in=180] (Q7);
\draw[arr,dashed,draw=cproved]   (Q7)--(geom);
\draw[spine] (Q5a)   to[out=0,in=90]   (H2);
\draw[arr]   (H2)    to[out=-90,in=0]  (geom);

\draw[spine] (Found) to[out=0,in=90] (Q1);
\draw[arr]   (O18)   to[out=10,in=180] (Q1);
\draw[arr]   (O22)   to[out=10,in=180] (Q1);
\draw[arr]   (O23)   to[out=10,in=180] (Q1);
\draw[arr]   (Q1)--(Q2);
\draw[arr]   (Q2)--(Q3);
\draw[arr]   (Q2)--(Q5a);
\draw[arr]   (Q5a)--(Q5aO2);
\node[font=\tiny\sffamily,text=cproved,right=2pt] at (Q5aO2.east)
  {\begin{tabular}{l}[H-$\mathcal{E}$1], [C]\\proved
\end{tabular}};
\draw[spine] (Q5a)--(Q5b);
\draw[arr]   (Q5b)--(Q6a);
\draw[arr]   (O31) to[out=0,in=-150] (Q6a);
\draw[arr]   (Q6a)--(Q6b);

\node[S] (Sp2)  at (-1.5*\dx,-5*\dy) {Spec2};
\node[P] (Grav) at (-1.5*\dx,-6*\dy) {Gravity};
\node[S] (Thm)  at (-1.5*\dx,-7*\dy) {Thermo};
\node[P] (Lor)  at (-1.5*\dx,-8*\dy) {Lorentz};

\draw[arr]   (WP) to[out=-90,in=90] (Sp2);
\draw[spine] (Sp2)--(Grav);
\draw[arr]   (Grav)--(Thm);
\draw[arr]   (Thm)--(Lor);

\node[P] (TopI) at (0,-8*\dy)        {TopInv};
\node[S] (SMcm) at (\dx,-8*\dy)      {SMcm};
\node[P] (Bell) at (2*\dx,-8*\dy)    {Bell};
\node[S] (Schw) at (3*\dx,-8*\dy)    {SchLamb};
\node[S] (Cosm) at (4*\dx,-8*\dy)    {Cosmol};
\node[S] (Supra)at (5*\dx,-8*\dy)    {Supra};

\draw[arr] (Found) to[out=-90,in=90] (TopI);
\draw[arr] (BI)    to[out=-90,in=90] (SMcm);
\draw[arr] (Found) to[out=-90,in=90] (Bell);
\draw[arr] (ENI)   to[out=-90,in=90] (Bell);
\draw[arr] (Found) to[out=-90,in=90] (Schw);
\draw[arr] (BI)    to[out=-90,in=90] (Cosm);
\draw[arr] (Found) to[out=-90,in=90] (Supra);

\node[S] (Q12) at (3*\dx,-11*\dy) {Q12};
\node[font=\tiny\sffamily,text=cstruct,right=2pt] at (Q12.east)
  {YM from $a_4$};
\draw[arr] (Grav) to[out=-90,in=135] (Q12);
\draw[arr] (Q6a)  to[out=200,in=60]  (Q12);

\node[S] (Q13) at (3*\dx,-12*\dy) {Q13};
\node[font=\tiny\sffamily,text=cstruct,right=2pt] at (Q13.east)
  {EYM + hierarchy};
\draw[arr] (Q12)  to[out=-90,in=90]  (Q13);
\draw[arr] (Grav) to[out=-90,in=150] (Q13);
\draw[arr] (BI)   to[out=-90,in=180] (Q13);

\node[S] (Q14) at (3*\dx,-13*\dy) {Q14};
\node[font=\tiny\sffamily,text=cstruct,right=2pt] at (Q14.east)
  {Fermions + chirality};
\draw[arr] (Q13) to[out=-90,in=90]  (Q14);
\draw[arr] (Grav) to[out=-90,in=160] (Q14);
\draw[arr] (BI)   to[out=-90,in=175] (Q14);

        \end{tikzpicture}
      }
      \caption{Logical dependency DAG of the Cosmochrony programme.
      Colour coding: \textcolor{cproved}{$\blacksquare$}~\sproved{},
        \textcolor{cstruct}{$\blacksquare$}~\sstruct{},
        \textcolor{cheur}{$\blacksquare$}~\sheur{},
        \textcolor{copen}{$\blacksquare$}~\sopen{}.
        Thick arrows indicate the main logical spine; thin arrows indicate supporting dependencies.
        Dashed arrows with labels abbreviate linear sub-chains.
        The dashed green arrow from Q7 leads to the geometric emergence closure block
        Q8--Q10 and U1, detailed in Figure~\ref{fig:geom}.
        The interactive version with clickable nodes is provided as a companion HTML file.}
      \label{fig:dag}
    \end{figure}

    \clearpage

    \begin{figure}[p]
      \centering
      \resizebox{\textwidth}{!}{%
        \begin{tikzpicture}[
          every node/.style={font=\small\sffamily},
          box/.style={draw, rounded corners=3pt, inner sep=5pt,
          minimum width=2.0cm, minimum height=0.7cm, align=center},
          P/.style={box, fill=green!8,  draw=cproved,  text=black},
          S/.style={box, fill=blue!6,   draw=cstruct,  text=black},
          spine/.style={-{Stealth[length=5pt]}, line width=1.2pt},
          arr/.style={-{Stealth[length=4pt]}, thin},
        ]

        \def\dx{3.2cm}
        \def\dy{1.4cm}

        % ── Inputs (left column) ──────────────────────────────
        \node[S] (Q5a)   at (0,0)          {Q5a};
        \node[P] (Q5aO2) at (\dx,0)        {Q5a-O2};
        \node[S] (Q5b)   at (0,-\dy)       {Q5b};
        \node[S] (O25)   at (-\dx,-2*\dy)  {O25};

        % ── Core chain (centre column) ───────────────────────
        \node[S] (Q7)  at (\dx,-2*\dy) {Q7};
        \node[S] (Q8)  at (2*\dx,-3*\dy){Q8\\{\tiny $A_Z\!=\!2$}};
        \node[P] (Q9)  at (\dx,-3*\dy) {Q9\\{\tiny [H-lift]}};
        \node[S] (Q10) at (\dx,-4*\dy) {Q10\\{\tiny $A_H\!\to\!2$}};
        \node[P] (U1)  at (\dx,-5*\dy) {U1\\{\tiny [U] proved}};
        \node[P] (W1)  at (2*\dx,-5*\dy){W1\\{\tiny [H-w] proved}};

        % Q11 and final result
        \node[S] (Q11) at (\dx+0.5*\dx,-6*\dy)
          {Q11\\{\tiny $A_\tau\!=\!2$}};
        \node[P,minimum width=4cm] (Met)
        at (\dx+0.5*\dx,-7*\dy)
          {$g^{\mu\nu}=\mathrm{diag}(-2,2,2,2)$};

        % ── Edges ────────────────────────────────────────────
        \draw[arr]   (Q5a)--(Q5aO2);
        \draw[spine] (Q5a)--(Q5b);
        \draw[arr]   (Q5a) to[out=0,in=90] (Q7);
        \draw[arr]   (Q5aO2) to[out=-90,in=90] (W1);
        \draw[arr]   (Q5b) to[out=0,in=135] (Q7);
        \draw[arr]   (Q5b) to[out=-45,in=90] (Q9);
        \draw[arr]   (Q5b) to[out=-90,in=90] (U1);
        \draw[arr]   (O25) to[out=0,in=180] (Q10);

        \draw[spine] (Q7)--(Q9);
        \draw[arr]   (Q7) to[out=0,in=90] (Q8);
        \draw[spine] (Q9)--(Q10);
        \draw[arr]   (Q8) to[out=-90,in=0] (Q10);
        \draw[spine] (Q10)--(U1);
        \draw[spine] (U1)--(W1);
        \draw[arr]   (Q5a) to[out=-45,in=90] (W1);

        \draw[spine] (U1)  to[out=-90,in=135] (Q11);
        \draw[arr]   (Q8)  to[out=-90,in=45]  (Q11);
        \draw[arr]   (W1)  to[out=-90,in=45]  (Q11);
        \draw[spine] (Q11) -- (Met);

        % ── Status annotations ───────────────────────────────
        \node[font=\tiny\sffamily,text=cproved,right=2pt] at (Q5aO2.east)
          {spectral atomicity};
        \node[font=\tiny\sffamily,text=cproved,right=2pt] at (Q9.east)
          {coercivity $\Rightarrow A_H\!>\!0$};
        \node[font=\tiny\sffamily,text=cproved,right=2pt] at (U1.east)
          {rate $O(q^{-1/2})$};
        \node[font=\tiny\sffamily,text=cproved,right=2pt] at (W1.east)
          {fibre-inv.\ $\Rightarrow$ uniform};

        \end{tikzpicture}
      }
      \caption{Geometric emergence sub-programme: logical chain from Q5a to the effective
      Lorentzian co-metric.
      \textbf{Q5a-O2}~\cite{Beau2026q5ao2}~(\sproved{}): spectral atomicity of $\mathrm{ran}(\Pi_q)$;
      proves [H-$\mathcal{E}$1] and [C]; closes all Q5a hypotheses except [H2].
      \textbf{Q9}~(\sproved{}): [H-lift] is a theorem under Q5a; coercivity gives $A_H>0$
        independently of the bridge.
        \textbf{Q8}~(\sstruct{}): $A_Z = C_{\mathfrak{su}(2)} = 2$ by Casimir rigidity;
        normalisation fixed by horizontal sector.
        \textbf{Q10}~(\sstruct{}): universality~[U] $\Rightarrow$ $\mathfrak{su}(2)$-isotropy
        $\Rightarrow$ $A_H \to 2$, conditional on~[U].
        \textbf{U1}~(\sproved{}): [U] proved with rate $O(q^{-1/2})$ from Weil-generator
        Lipschitz bound and BFS--Carnot--Carath\'eodory convergence (Q5b).
        \textbf{W1}~(\sproved{}): [H-w] proved as a structural consequence of fibre-invariance
        ($\mathcal{O}=\mathrm{Im}\,\Pi$), quantitative control from~U1.
        The effective metric $g^{\mu\nu} = \mathrm{diag}(-A_\tau,2,2,2)$ is established
        under the Q5a hypotheses; [H2] is the sole remaining open hypothesis.}
      \label{fig:geom}
    \end{figure}
    \label{sec:inventory}

    Table~\ref{tab:inventory} lists all papers in the programme.
    The \textbf{Key} column gives the \texttt{cosmochrony-bibliography} citation key.

    \setlength\LTleft{0pt}
    \setlength\LTright{0pt}
    \begin{longtable}{@{}p{1.45cm}p{3.4cm}p{1.5cm}p{6.5cm}p{1.3cm}@{}}
      \label{tab:inventory}\\
      \toprule
      \textbf{Label} & \textbf{Short title} & \textbf{Key} & \textbf{Main contribution} & \textbf{Status}\\
      \midrule
      \endhead
      \midrule\multicolumn{5}{r}{\small\itshape continued\ldots}\\\midrule
      \endfoot
      \bottomrule
      \endlastfoot
      WP & White Paper & \cite{Cosmochrony} &
      Programme overview; substrate~$\chi$; iterated projection; BI constraint; relaxation cascade &
      \sstruct \\[3pt]
      ENI & Emergence \& non-injectivity & \cite{Beau2026l} &
      No-go: genuine emergence $\Leftrightarrow$ $\Pi$ non-injective; projection entropy $S_\Pi$ &
      \sproved \\[3pt]
      Found & Foundation & \cite{Beau2026m} &
      Axioms A1--A4; derives $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ and $V_\rho$ as theorems (Thm~5.6);
      v1.10: co-metric $g^{\mu\nu}=\mathrm{diag}(-2,2,2,2)$ noted; relation to HJ, symplectic,
      WKB, FRG formalisms &
      \sproved \\[3pt]
      HeisStr & Heisenberg structure & \cite{Beau2026HeisenbergStructure} &
      Detailed proof of Found. Thm~5.6; uncertainty principle from A3 alone &
      \sproved \\[3pt]
      noscale & No external scale & \cite{Beau2026j} &
      No independent dimensional parameter beyond $c_\chi$ &
      \sproved \\[3pt]
      \midrule
      BornInfeld & Born--Infeld geometry & \cite{Beau2026c} &
      BI action as unique minimal bounded-flux representation &
      \sproved \\[3pt]
      SpAdm & Spectral admissibility ($Q_8$) & \cite{Beau2026a1} &
      $A^{\max}_n = c_\chi/\sqrt{\lambda_n}$; first tractable instance &
      \sproved \\[3pt]
      SpCap & Spectral capacity & \cite{Beau2026a2} &
      Capacity functional $\mathcal{C}(G,S)$; binary-polyhedral maximality proved via
      adjoint identity $\hat{A}_{\mathrm{adj}} = 2M - I$ and icosahedral isotropy &
      \sproved \\[3pt]
      SpGram & Gram rigidity (v1.0.1) & \cite{Beau2026a3} &
      Neutral-generator geometry from $G_{st} = -\tfrac{1}{2}\chi_\rho(st)$ &
      \sproved \\[3pt]
      3Gen & Three generations & \cite{Beau2026a4} &
      Three-generation structure from ADE stratigraphic levels &
      \sstruct \\[3pt]
      SpRel & Spectral relaxation & \cite{Beau2026a5} &
      $\Lambda_{\mathrm{proj}} \asymp \lambda_2$ for LPS expander families &
      \sproved \\[3pt]
      \midrule
      O1 & Variable-valence graphs & \cite{Beau2026a6} &
      LPS saturation is a fixed-valence artefact; growing valence restores window &
      \sproved \\[3pt]
      O3 & Mass hierarchy & \cite{Beau2026a7} &
      First SM connection: $\beta^* \in (0.09, 0.13)$ from lepton mass ratios &
      \sstruct \\[3pt]
      O4 & Upper bound $\beta \leq 1$ & \cite{Beau2026a8} &
      BI flux $+$ Cheeger $\Rightarrow \beta \leq 1$ &
      \sproved \\[3pt]
      O5 & Rep-theoretic obstruction & \cite{Beau2026a9} &
      Fixed-repr.\ approaches cannot close the $\beta$ gap &
      \sproved \\[3pt]
      O6 & Matrix redundancy & \cite{Beau2026a10} &
      Matrix-level confinement of cascade exponent &
      \sproved \\[3pt]
      O7 & Continuum target & \cite{Beau2026a11} &
      Target: $\delta \in [7.4, 10.6]$ on 3-step fingerprints &
      \sstruct \\[3pt]
      O8 & LPS geometric obstruction & \cite{Beau2026a12} &
      Exponential shell growth $\Rightarrow$ usable window $= O(\log q)$ BFS steps &
      \sproved \\[3pt]
      \midrule
      O9 & Heisenberg graphs & \cite{Beau2026a13} &
      Structural transition: $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ with $|B_n| \sim n^4$ replaces LPS &
      \sproved \\[3pt]
      O10 & Large-$q$ computation & \cite{Beau2026a14} &
      Confirms $n^4$ growth; TensorSketch obstruction identified &
      \sproved \\[3pt]
      O11 & Fourier-character proxy & \cite{Beau2026a15} &
      Bidimensional proxy overcomes TensorSketch obstruction &
      \sstruct \\[3pt]
      O12 & Exact Weil blocks & \cite{Beau2026a16} &
      $\hat\delta_{\mathrm{exact}} \approx 4.3$--$4.8$ for $q \leq 211$; final obstruction resolved &
      \sproved \\[3pt]
      O13 & Extended prime range & \cite{Beau2026a17} &
      $\hat\delta(q): 4.80 \to 3.59$; finite-size hypothesis refuted &
      \sproved \\[3pt]
      O14 & Observable-class correction & \cite{Beau2026a18} &
      Corrects $\delta \mapsto \beta^*$ via block normalisation &
      \sstruct \\[3pt]
      O15 & Block-level no-go & \cite{Beau2026a19} &
      No reweighting of individual blocks reaches $\delta \in [7.4, 10.6]$ (Cor.~4.8) &
      \sproved \\[3pt]
      \midrule
      O16 & Pair observable & \cite{Beau2026a20} &
      $\sigma_{\mathrm{pair}} = \sigma_c \sigma_{q-c}$;
      exponent doubling $\delta_{\mathrm{pair}} \approx 7.44$ &
      \sstruct \\[3pt]
      O17 & Structural derivation of pair & \cite{Beau2026a21} &
      $\rho_{q-c} = \bar\rho_c$ forced by fibre admissibility: pair is derived, not postulated &
      \sproved \\[3pt]
      O18 & BI parity involution & \cite{Beau2026a22} &
      Minimal fibre condition $\{\chi,-\chi\}$; BI parity is the unique global symmetry of $S_{\mathrm{BI}}$ &
      \sproved \\[3pt]
      O19 & Canonical normalisation & \cite{Beau2026a23} &
      $r(c,q)$ does not affect $\delta_{\mathrm{pair}}$; observable pipeline-independent &
      \sproved \\[3pt]
      O20 & Persistence criterion & \cite{Beau2026a24} &
      Dynamical selection of admissible modes via projective persistence &
      \sstruct \\[3pt]
      O21 & Shell saturation & \cite{Beau2026a25} &
      Observable rank $n_3^{\mathrm{obs}}$ via $\Sigma_c(n_3)=3$;
      transfer $\delta_{\mathrm{pair}} \to \beta^*$ &
      \sstruct \\[3pt]
      O22 & Projection locking & \cite{Beau2026a26} &
      BI projection locking forces $n_3^{\mathrm{obs}}$ onto a BFS shell (Thm~3.2) &
      \sproved \\[3pt]
      O23 & Quaternionic minimality & \cite{Beau2026a27} &
      $\Sigma_c(n_3)=3$ from quaternionic maximality of neutral generators &
      \sproved \\[3pt]
      O24 & Observable rank rigidity & \cite{Beau2026a28} &
      Verticality Lemma; unconditional transfer
      $c_\chi \to \delta_{\mathrm{pair}} \to \beta^* \approx 0.126$ (Cor.~4.2) &
      \sproved \\[3pt]
      \midrule
      O25 & Numerical campaign & \cite{Beau2026a29} &
      $\bar\delta_{\mathrm{pair}} \in \{8.89, 9.98, 9.55, 9.13, 8.78\}$ for $q \in \{29,61,101,151,211\}$;
      inter-pair $\sigma_q: 0.54 \to 0.11$; $\delta_{\mathrm{corr}} \in [7.7,9.0] \subset [7.4,10.6]$ &
      \sstruct \\[3pt]
      O26 & Quadratic completion & \cite{Beau2026a30} &
      Dictionary: Weil blocks $\leftrightarrow$ rank-1 matrices in $M_2(\mathbb{C})$;
      connects $\Heis_3$ to $2I \subset \SU(2)$ &
      \sstruct \\[3pt]
      O27 & Quaternionic rigidity & \cite{Beau2026a31} &
      Every admissible $\Phi_{q,\rho}$ satisfying three structural constraints factors through
      $\mathfrak{su}(2)$ &
      \sproved \\[3pt]
      O28 & Window calibration \& $r_{\mathrm{eff}}$ & \cite{Beau2026a32} &
      $n_1(q)/q$ decreasing (Scenario~S2); $\delta_{\mathrm{corr}} \in [7.4,10.6]$ confirmed;
      $r_{\mathrm{eff}}=3$ in $\mathrm{End}(H_{\mathrm{eff}})$, eigenstructure
      $[1:\tfrac{1}{2}:\tfrac{1}{2}]$ invariant across all pairs and $q \in \{61,101,151\}$ &
      \sstruct \\[3pt]
      O29 & Symmetric rank formula \& sector ID & \cite{Beau2026a33} &
      BI parity forces $M_j \in \mathrm{Sym}(V_\rho,\mathbb{C})$;
      $r_{\mathrm{eff}} = d_\rho(d_\rho+1)/2$; unique inversion at $r_{\mathrm{eff}}=3$ gives
      $d_\rho=2$ (spin-$\tfrac{1}{2}$); confirmed for $q \in \{61,101,151,211\}$;
      $q=101$ anomaly resolved by multi-sample analysis &
      \sstruct \\[3pt]
      O30 & Eigenvalue ratio $\lambda_1/\lambda_2$ & \cite{Beau2026a34} &
      BI parity forces equatorial constraint $|\alpha_j|=|\beta_j|$;
      phase-independent central component gives
      $\mathcal{C}_c = \langle r^4\rangle\,\mathrm{diag}(1/4,1/2,1/4)$;
      ratio $[1:\tfrac{1}{2}:\tfrac{1}{2}]$ derived analytically;
      factor of~$2$ is purely structural (Carnot degree-$2$ of $Z=[X,Y]$) &
      \sproved \\[3pt]
      O31 & SU(3) from colour triplets & \cite{Beau2026a35} &
      Hurwitz obstruction ($d_\rho=3$ cannot arise from single-fibre argument, proved);
      colour triplets exist iff $q\equiv 1\pmod{3}$ (proved);
      metaplectic intertwining proves $\sigma_c=\sigma_{\omega c}$ on $\mathcal{S}_q^{(3)}$
      (proved, Thm~4.4); conditional on [H-color],
      $\SU(3)$ is the unique triplet symmetry group (proved; $\mathrm{U}(3)$, $\mathrm{SO}(3)$,
      $\mathrm{U}(2)$, $G_2$ excluded); $G_{\mathrm{SM}}$ derived for $\mathcal{S}_q^{(3)}$ &
      \sstruct \\[3pt]
      O32 & [H-color] numerical test & \cite{Beau2026a36} &
      [H-color] passes for $q\in\{61,151,211\}$; $C_{\mathrm{color}}$ rank~1;
      $\delta_{\mathrm{tri}}\approx 3\delta_c$;
      $\Hcolor_{\mathrm{eff}}$ proved analytically in expectation (Prop.~avg-hcolor,
      $\mathbb{E}[\sigma_c]=\mathbb{E}[\sigma_{\omega c}]+O(q^{-1})$);
      pointwise proof open &
      \sstruct \\[3pt]
      PTO & Temporal ordering & \cite{Beau2026pto} &
      $I(n) = \sigma_{\mathrm{pair}}(0) - \sigma_{\mathrm{pair}}(n)$ is a non-decreasing
      temporal proxy; confirmed for $q \in \{29, 61, 101, 151, 211\}$ &
      \sstruct \\[3pt]
      \midrule
      Q1 & Phase coherence & \cite{Beau2026q1} &
      Phase coherence from admissibility (Thm~2.7);
      singlet correlator and Tsirelson bound derived &
      \sproved \\[3pt]
      Q2 & Beyond spin-$\tfrac{1}{2}$ & \cite{Beau2026q2} &
      Spin-$\tfrac{3}{2}$ quantum structure; $\SU(2)$ as admissibility fixed point &
      \sproved \\[3pt]
      Q3 & Universal spin-$j$ singlet & \cite{Beau2026q3} &
      Schur + BI indiscernibility identify proto-state as singlet $|\Omega_j\rangle$ for all
      $j \in \{\tfrac{1}{2},1,\tfrac{3}{2},2,\tfrac{5}{2}\}$; universal correlator and Born rule
      derived; closes Q2 open step &
      \sproved \\[3pt]
      Q5a & Large-$q$ operator limit & \cite{Beau2026q5a} &
      Mosco convergence $\mathcal{E}_q \to L_\Pi = -A\partial_x^2$; conditional on [H2].
      v2.0: [H1] established on admissible sector (not needed in full generality);
      [H-$\mathcal{E}$1] and [C] proved by Q5a-O2~\cite{Beau2026q5ao2}; [H2] proved by H2~paper:
      all hypotheses verified on the admissible sector &
      \sstruct \\[3pt]
      Q5a-O2 & Spectral atomicity \& Mosco closure & \cite{Beau2026q5ao2} &
      Admissible sector spectrally atomic: $\mathrm{ran}(\Pi_q^{(c)}) =
      \mathrm{span}\{e_0, e_{\xi_c}, e_{q-\xi_c}\}$, $\xi_c/q \to \omega_c \neq 0$.
      Proves [H-$\mathcal{E}$1'] (scaled coercivity, $\beta=1$ optimal) and [C]
      (Mosco compactness via Bolzano--Weierstrass in $\mathbb{C}^2$, no Nash inequality needed).
      Numerical confirmation $K_q=1$ at machine precision for $q \in \{29,61,101,151\}$ &
      \sproved \\[3pt]
      Q5b & 4D Lorentzian geometry & \cite{Beau2026q5b} &
      BFS stratification of $\Heis_3(\mathbb{R}) \to$ 4D Lorentzian spacetime; conditional &
      \sstruct \\[3pt]
      Q6a & Gauge structure & \cite{Beau2026q6a} &
      $\mathrm{U}(1)$ and $\SU(2)$ from fibre fixed points;
      $\SU(3)\times\SU(2)\times\mathrm{U}(1)$ derived (O31~\cite{Beau2026a35},
      conditional on [H-color]) &
      \sstruct \\[3pt]
      Q6b & Effective spacetime & \cite{Beau2026q6b} &
      $g^{\mu\nu}=\mathrm{diag}(-2,2,2,2)$ from $\Pi_q$;
      Schwarzschild from flux conservation; Einstein equations as consistency conditions;
      closes chain $\Pi_q\to\mathcal{L}_\Pi\to g^{\mu\nu}\to G_{\mu\nu}$;
      [H-lift] closed by Q9 &
      \sstruct \\[3pt]
      Q7 & Dimensional bridge & \cite{Beau2026q7} &
      $H_{\mathrm{eff}} \cong \mathrm{Sym}^2(V_\rho)$; $[F_c, L_{\mathrm{Weil}}]=0$;
      bridge non-obstruction (Case~3 excluded by Q9); $A_z = C_{\mathfrak{su}(2)} = 2$;
      uniqueness of $\varphi$ up to scalar &
      \sstruct \\[3pt]
      Q8 & Casimir rigidity & \cite{BeauQ8} &
      $A_Z = C_{\mathfrak{su}(2)} = 2$ unconditionally under Q5a;
      $\lambda$ fixed by horizontal sector consistency;
      $g^{\mu\nu} = \mathrm{diag}(-A_\tau,2,2,2)$ established &
      \sstruct \\[3pt]
      Q9 & [H-lift] proved & \cite{Beau2026q9} &
      Kinetic-sector identification: modulation generator suppressed at rate $O(q^{-1/2})$;
      [H-lift] is a theorem under Q5a; $A_H > 0$ proved by coercivity, independently of bridge &
      \sproved \\[3pt]
      Q10 & Asymptotic isotropy & \cite{Beau2026q10} &
      $A_H(q) \to 2$ with $|A_H - 2| \leq C\,\varepsilon(q)$;
      universality~[U] $\Rightarrow$ $\mathfrak{su}(2)$-isotropy $\Rightarrow$ Casimir;
      bridge conjecture resolved (isotropic case) under [U] &
      \sstruct \\[3pt]
      U1 & Universality [U] proved & \cite{Beau2026u1} &
      $\varepsilon(q) = O(q^{-1/2})$ from Weil-generator Lipschitz bound and
      BFS--Carnot--Carathéodory convergence; no BI input required for small-$\theta$ regime &
      \sproved \\[3pt]
      W1 & [H-w] proved & \cite{Beau2026w1} &
      $a_q(s) \to A > 0$ uniformly in $s$: fibre-invariance of admissible observables
      ($\mathcal{O}=\mathrm{Im}\,\Pi$) is the structural origin; U1 controls the rate $O(q^{-1/2})$;
      after W1 + Q5a-O2~\cite{Beau2026q5ao2}, open Q5a hypotheses reduced to [H2] only &
      \sproved \\[3pt]
      H2 & [H2] proved & \cite{Beau2026h2} &
      Strong convergence $\hat{X}_q \to x$, $\hat{P}_q \to -i\partial_x$ on
      $\Heis_3(\mathbb{Z}/q\mathbb{Z})$: quantitative Poisson aliasing lemma (rate $O(q^{-1})$),
      discrete Sobolev identity, quasi-isometry of sinc embedding;
      closes last open hypothesis of Q5a Theorem~7.1 &
      \sproved \\[3pt]
      Q11 & Temporal Casimir rigidity & \cite{Beau2026q11} &
      Closes Q5b open problem~O3: Schur rigidity forces $A_\tau = C_{\mathfrak{su}(2)} = 2$;
      effective Lorentzian co-metric fully determined:
      $g^{\mu\nu} = \mathrm{diag}(-2,2,2,2) \propto \eta^{\mu\nu}$ &
      \sstruct \\[3pt]
      Q12 & Yang--Mills from $a_4$ & \cite{Beau2026q12} &
      Seeley--DeWitt $a_4 \supset \tfrac{1}{12}\mathrm{Tr}(F^2)$;
      vertical variation $\delta_\mathcal{A} S_\Pi = 0$ yields $D_\mu F^{a\mu\nu} = 0$;
      induced coupling $g_{\mathrm{YM}}^{-2} \sim \log(\Lambda/\mu)$;
      gauge--gravity hierarchy structural (\sproved{} for $a_4$ derivation;
      conditional on Q6a for $G_\Pi$) &
      \sstruct \\[3pt]
      Q13 & Gauge--gravity spectral synthesis & \cite{Beau2026q13} &
      Joint $\delta_{g,\mathcal{A}} S_\Pi = 0$ yields coupled Einstein--Yang--Mills system;
      $a_6$ cross-coupling $R_{\mu\nu\rho\sigma}F^{\mu\nu}F^{\rho\sigma}$ (suppressed by
      $\ell_{\mathrm{sp}}^2$); Eddington--Born--Infeld joint completion;
      hierarchy ratio $G_N g_{\mathrm{YM}}^2 \sim \ell_{\mathrm{sp}}^2/(\dim V)\cdot
      [\log(\Lambda/\mu)]^{-1}$ without fine-tuning &
      \sstruct \\[3pt]
      Q14 & Fermionic matter \& chirality & \cite{Beau2026q14} &
      Admissible spinor bundle $S_\Pi$ reproduces $\SU(2)_L \times U(1)_Y$;
      projected Dirac endomorphism $E_\Pi$ enforces $V{-}A$ chirality under spinorial BI parity;
      $\gamma_5$-weighted $a_4$ fixes hypercharge by anomaly cancellation;
      $\sigma_c(n_3) = 3$ yields three-generation factor $\mathbb{C}^3_{\mathrm{gen}}$;
      quark colour sector conditional on [H-color] &
      \sstruct \\[3pt]
      \midrule
      Spec2 & Relational spacetime & \cite{Beau2026a} &
      Operational metric from graph Laplacians; spacetime from spectral correlations &
      \sstruct \\[3pt]
      Gravity & IR Einstein response + BI UV completion & \cite{Beau2026h} &
      $G_{\mu\nu} = 8\pi G_N T^{(\Pi)}_{\mu\nu}$ from $\delta S_\Pi/\delta g$ at leading IR order;
      unique BI determinantal UV completion &
      \sproved \\[3pt]
      Thermo & Spectral thermodynamics & \cite{Beau2026Thermodynamics} &
      Local spectral first law; Einstein equation as spectral equilibrium condition &
      \sstruct \\[3pt]
      Lorentz & Gravitational waves & \cite{Beau2026i} &
      Lorentzian completion; causal propagation; GW spectrum &
      \sproved \\[3pt]
      TopInv & Topological invariants & \cite{Beau2026k} &
      Charge quantisation ($\pi_1 \cong \mathbb{Z}$), no monopoles, chirality (Hopf fibration) &
      \sproved \\[3pt]
      SMcm & Charge, mass, inertia & \cite{Beau2026e} &
      Mass and charge as BI-saturated responses &
      \sstruct \\[3pt]
      Bell & Bell non-locality & \cite{Beau2026b} &
      Bell violations from non-injectivity alone &
      \sproved \\[3pt]
      SchLamb & Fine-structure constant & \cite{Beau2026f} &
      $\alpha$ as projective invariant; Lamb shift and Schwinger correction &
      \sstruct \\[3pt]
      Cosmol & Rotation curves / Hubble & \cite{Beau2026d} &
      Flat rotation curves and Hubble tension from a common effective mechanism &
      \sstruct \\[3pt]
      Supra & Superconductivity & \cite{Beau2026g} &
      Projective phase locking as origin of superconducting coherence &
      \sstruct \\[3pt]
    \end{longtable}

  \section{Open Problems}
  \label{sec:open}

  \subsection{Branch II (O-Series)}

    \paragraph{Extension of O29 to larger primes.}
      The symmetric rank formula is confirmed for $q \in \{61, 101, 151, 211\}$
      ($105/105$ pairs at $q=211$, $100\%$, multi-sample confirmed).
      Extension of the numerical computation to $q \in \{307, 401\}$ is pending.

    \paragraph{Non-conjugate block protocol.}
      A measurement protocol using non-conjugate block data (e.g.\ the $c$-block at
      two independent primes) would probe the full rank $d_\rho^2 = 4$ and provide
      a direct test of O26 Criterion~5.4 in its original formulation.

    \paragraph{Analytical control of $n_1(q)/q$.}
      The BFS window ratio $n_1(q)/q$ decreases monotonically through $q = 211$
      (O28, Scenario~S2); the asymptotic constant $\hat\alpha$ is bounded below by $0.062$ (updated from O28
      with $q=211$ data) but not yet stabilised.

    \paragraph{Notation consolidation: $c_\chi \to c_{\mathrm{BI}}$.}
      A coordinated rename of the BI saturation constant across all papers is planned and deferred
      pending consistency with already-deposited O-series papers.

  \subsection{Branch III (Q-Series and Applications)}

  \paragraph{Bridge existence at finite $q$ (Q7--Q10).}
    The asymptotic isotropy $A_H \to 2 = A_Z$ is proved by Q10 and U1 (conditionally on~[U]),
    establishing the isotropic limit of Q7 Conjecture~4.7.
    What remains open is the finite-$q$ structural question: whether an explicit
    $\mathfrak{su}(2)$-equivariant isomorphism $\varphi_q : \mathrm{Sym}^2(V_\rho) \xrightarrow{\sim} W_{\mathrm{sp}}$
    exists at each prime~$q$, not only in the limit.

  \paragraph{$\pi_2(\mathcal{C}_{\mathrm{eff}}) = 0$ beyond the canonical model (TopologicalInvariants, Remark 4.2).}
    General proof of this topological property is open.

  \paragraph{Full SM gauge group: [H-color] and O32 (Q6a, O31).}
    O31~\cite{Beau2026a35} derives $\SU(3)\times\SU(2)\times\mathrm{U}(1)$ as a composite of
    admissibility fixed points unconditionally for the colour-adapted Cayley graph, and
    conditionally on Hypothesis~[H-color] for the standard graph.
    O32~\cite{Beau2026a36} confirms [H-color] numerically for $q\in\{61,151,211\}$:
    all three pass $R \leq 1$ relative to the control noise floor
    $\mathtt{ctrl\_ref} = 3.81\times10^{-3}$ (calibrated from $q\in\{29,101\}$);
    $q=307$ is in progress.
    What remains open: analytical derivation of [H-color] from Foundation axioms;
    transfer chain $\delta_{\mathrm{tri}} \to \alpha_s$ (strong coupling constant);
    identification of quarks as stable projected configurations carrying colour quantum numbers.

  \paragraph{Baryon-to-photon ratio (SMchargemass).}
    Quantitative derivation of $\eta \sim 10^{-10}$ is open.

  \paragraph{$V-A$ chiral structure and fermionic matter (Q14).}
    Q14~\cite{Beau2026q14} addresses the formal derivation of the $V{-}A$ coupling:
    the projected Dirac endomorphism $E_\Pi$, under the spinorial lift of BI parity,
    is left-admissible and enforces chiral selection.
    Hypercharge is not a free parameter but is fixed by anomaly-cancellation constraints
    on the $\gamma_5$-weighted $a_4$ Seeley--DeWitt coefficient.
    The three-generation multiplicity follows from $\sigma_c(n_3) = 3$.
    Residual open points: Lorentzian extension of the projected Dirac operator,
    explicit mass generation mechanism, and quark colour sector (conditional on [H-color]).

  \paragraph{Gauge--gravity synthesis (Q12 $\to$ Q13).}
    Q12 establishes Einstein gravity and Yang--Mills dynamics as independent ($a_2$ and $a_4$)
    sectors of the single functional $S_\Pi[g,\mathcal{A}]$.
    Q13~\cite{Beau2026q13} completes this synthesis: the joint variational problem
    $\delta_{g,\mathcal{A}} S_\Pi = 0$ yields the coupled Einstein--Yang--Mills system,
    the precise hierarchy ratio $G_N g_{\mathrm{YM}}^2 \sim \ell_{\mathrm{sp}}^2/(\dim V)
    \cdot [\log(\Lambda/\mu)]^{-1}$, and the Eddington--Born--Infeld completion of the
    joint functional.
    Residual open points: EBI tensor $\Xi_{\mu\nu}$ ambiguity (subleading),
    numerical $a_6$ coefficients, Lorentzian extension of the joint EBI functional,
    and extension to include projected matter currents $J^{a\nu}$.

  \paragraph{Yang--Mills uniqueness for SU(3) (Q12, O31).}
    Q12 derives the Yang--Mills equations for any compact $G_\Pi$ from the $a_4$
    heat-kernel coefficient; the SU(3) sector is inherited from O31/Q6a.
    What remains open is the internal SU(3) uniqueness problem (O31 §9.2):
    showing that the SU(3) gauge dynamics emerge \emph{uniquely} from the colour
    triplet co-admissibility structure, without inputting the group as data.

  \paragraph{Thermodynamics: Lorentzian extension and matter coupling.}
    The local spectral first law is derived in the Riemannian setting.
    Analytic continuation and the explicit form of $W_\Pi$ for matter fields are open.

    \clearpage

  \section{Conclusion}

  The Cosmochrony programme has established a coherent, multi-level derivation of physical structure
  from a single primitive.
  Branch~I (Foundation, ENI, HeisenbergStructure~\cite{Beau2026HeisenbergStructure}
  ) is formally closed: the Weil representation of
  $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ is a theorem.
  The binary-polyhedral maximality conjecture (SpectralCapacity~\cite{Beau2026a2}) is proved:
  $2I$ uniquely maximises $\mathcal{C}_\alpha(G,S)$ for all $\alpha > 0$ among finite $\SU(2)$ subgroups
  with neutral generating sets, closing the precursor programme for the O-series.
  Branch~II (O-series) has closed the unconditional transfer chain $c_\chi \to \delta_{\mathrm{pair}} \to \beta^*$
  analytically~(O24) and numerically validated for $q \in \{29, 61, 101, 151, 211\}$~(O25).
  The spin-$\tfrac{1}{2}$ sector identification is complete~(O29): the symmetric rank formula
  $r_{\mathrm{eff}} = d_\rho(d_\rho+1)/2$ uniquely identifies $d_\rho = 2$ from the observed $r_{\mathrm{eff}} = 3$,
  confirmed numerically for $q \in \{61, 101, 151\}$.
  The invariant eigenvalue ratio $\lambda_1/\lambda_2 = 2$ of the per-pair covariance is
  now analytically derived~(O30): the Born--Infeld parity anti-linearity forces an equatorial
  constraint on the admissible fibre, and the factor of~$2$ is purely structural---the squared
  symmetric-tensor normalisation of the Carnot-degree-$2$ central generator $Z=[X,Y]$.
  O31 develops the structural framework for SU(3): the metaplectic intertwining of
  $\Heis_3(\mathbb{Z}/q\mathbb{Z})$ forces triplet co-admissibility unconditionally for the
  colour-adapted Cayley graph, and SU(3) is thereby identified as the symmetry group of the
  co-admissible colour triplet, conditional on Hypothesis~[H-color] for the standard graph.
  Branch~III (Q-series and companions) derives quantum mechanics, spacetime, and SM observables
  at the structural level, with several results conditional on explicitly stated hypotheses.
  The $\SU(2)$ quantum sector is now complete: Q3 closes the general-$j$ open step of Q2 by
  identifying the proto-state as the singlet for all five admissible sectors of $2I$ via
  Schur's lemma, and derives the universal correlator $E(\hat{a},\hat{b}) = -j(j+1)/3\cdot(\hat{a}\cdot\hat{b})$
  and Born rule for $j \in \{\tfrac{1}{2}, 1, \tfrac{3}{2}, 2, \tfrac{5}{2}\}$ (\sproved).
  The geometric emergence sub-programme has advanced substantially: Q9 proves [H-lift] and
  $A_H > 0$ (unconditionally under Q5a); Q10 proves $A_H \to 2$ under spectral universality~[U];
  U1 proves [U] with rate $O(q^{-1/2})$ from BFS convergence and Weil-generator stability;
  W1 proves [H-w] as a structural consequence of the fibre-invariance of admissible observables.
  The effective Lorentzian co-metric $g^{\mu\nu} = \mathrm{diag}(-2, 2, 2, 2) \propto \eta^{\mu\nu}$
  ($A_\tau = 2$ from Q11~\cite{Beau2026q11}) is thereby established under the Q5a foundational hypotheses and~[U].
  Q12~\cite{Beau2026q12} completes the spectral derivation of gauge dynamics:
  the Seeley--DeWitt $a_4$ coefficient of the operator $A_{g,\mathcal{A}}$ on the
  admissible vector bundle contains the Yang--Mills density $\tfrac{1}{12}\mathrm{Tr}(F^2)$,
  and the vertical variation $\delta_\mathcal{A}S_\Pi = 0$ yields $D_\mu F^{a\mu\nu} = 0$.
  Q13~\cite{Beau2026q13} completes the gauge--gravity synthesis: the joint variational problem
  $\delta_{g,\mathcal{A}} S_\Pi = 0$ yields the coupled Einstein--Yang--Mills system, and the
  gauge--gravity hierarchy $G_N g_{\mathrm{YM}}^2 \sim \ell_{\mathrm{sp}}^2/(\dim V)\cdot
  [\log(\Lambda/\mu)]^{-1} \ll 1$ emerges as a structural consequence of the spectral
  stratification ($a_2$ quadratic vs.\ $a_4$ logarithmic UV divergence), without fine-tuning.
  Q14~\cite{Beau2026q14} extends this to the fermionic sector: the admissible Weil module
  induces a spinor bundle $S_\Pi$ reproducing $\SU(2)_L \times U(1)_Y$; the projected Dirac
  endomorphism $E_\Pi$ enforces $V{-}A$ chirality under the spinorial lift of BI parity;
  hypercharge is fixed by anomaly-cancellation constraints on the $\gamma_5$-weighted $a_4$
  coefficient; and the saturation invariant $\sigma_c(n_3) = 3$ yields a gauge-singlet
  three-generation factor $\mathbb{C}^3_{\mathrm{gen}}$.
  Together, Q12--Q14 establish that the bosonic gauge and gravitational fields and the
  fermionic matter content of the Standard Model arise from a single structural source:
  the non-injective projection admissibility constraint on the Weil module.
  The Cosmochrony programme can now be stated in one sentence: it is a \emph{spectrally
  stratified theory of emergent interactions}, in which the type of a fundamental interaction
  is determined by the Seeley--DeWitt order at which the admissible operator responds.
  Q5a v2.0 establishes that [H1] is not needed in full generality on the admissible sector.
  Q5a-O2~\cite{Beau2026q5ao2} proves spectral atomicity of the admissible sector and closes [H-$\mathcal{E}$1] and [C]:
  each conjugate pair contributes exactly three pure Fourier modes, coercivity at the optimal
  diffusive scale follows from the non-zero limiting frequency, and Mosco compactness reduces to
  Bolzano--Weierstrass in $\mathbb{C}^2$.
  The H2 paper proves the last open hypothesis [H2] (strong convergence of the rescaled Weil
  generators $\hat{X}_q \to x$ and $\hat{P}_q \to -i\partial_x$) via a quantitative Poisson
  aliasing lemma and a discrete Sobolev identity; all hypotheses of Q5a Theorem~7.1 are
  verified on the admissible sector, and the large-$q$ convergence theorem holds unconditionally.

  For an external reader, three entry sequences are suggested.
  For the quantum structure thread:
  ENI $\to$ Foundation $\to$ O18 $\to$ O22 $\to$ O23 $\to$ Q1.
  For the spectral mass hierarchy thread:
  ENI $\to$ Foundation $\to$ O16 $\to$ O24.
  For the spacetime thread:
  Spectral2 $\to$ Gravity $\to$ (Thermodynamics or Lorentz);
  for the geometric emergence thread:
  Q5a $\to$ Q5b $\to$ Q7 $\to$ Q8 $\to$ Q9 $\to$ Q10 $\to$ U1 $\to$ W1 $\to$ H2 $\to$ Q11.

  \clearpage
  \bibliography{cosmochrony-bibliography}

\end{document}
